---
title: "figures"
author: "Herault"
date: "19/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## env
```{r cars}
suppressMessages(library(ggplot2))
suppressMessages(library(Seurat))
suppressMessages(library(monocle))
#suppressMessages(library(BoolNet))
suppressMessages(library(dplyr))
suppressMessages(library(igraph))
suppressMessages(library(plyr))
suppressMessages(library(stringr))
suppressMessages(library(grid))
suppressMessages(library(gridExtra))
suppressMessages(library(RColorBrewer))
#suppressMessages(library(gProfileR))
suppressMessages(library(gplots))
suppressMessages(library(reshape2))
#suppressMessages(library(ggpmisc))
suppressMessages(library(ggthemes))
suppressMessages(library("readxl"))


if (!requireNamespace("ggVennDiagram", quietly = TRUE))
  install.packages("ggVennDiagram",repos='http://cran.us.r-project.org')

suppressMessages(library("ggVennDiagram"))

# if (packageVersion("Seurat") != "3.2.2")
#   remotes::install_version("Seurat", version = "3.2.2",upgrade = FALSE,repos='http://cran.us.r-project.org')

source("../R_src/computeDiffFun.R")

```

## load results

```{r pressure, echo=FALSE}
interactionsTable0 <- read.table("../output/regulonAnalysis/mainRegulonTable.tsv") 
tfTested <- read.table("../output/publicData/mm_mgi_tfs.txt")
tfSelected <- read.table("../input/selectedTF.txt")
seurat <- readRDS("../../herault_et_al/scHSC_herault/report/seurat_report.rds")
monocle <- readRDS("../../herault_et_al/scHSC_herault/report/monocle_report.rds")

# Loading regulon score table
regulonTable <- read.csv("../output/ScenicRNA_multipleRuns/AUCell_maskDropouts/regulons_enrichment.csv",row.names = 1,check.names = F)

# only analyse postive regulons score

regulonTable <- regulonTable[,colnames(regulonTable)[which(endsWith(colnames(regulonTable),suffix = "+)"))]]

# Adding regulon scores to metadata

# store the data in a new assay in the seurat object of ordered cells
auCell_data <- t(regulonTable)

seurat[["AUCell"]] <- CreateAssayObject(data=auCell_data)

```

## table on regulon results
```{r}
allRegulons <- names(rjson::fromJSON(file = "../output/ScenicRNA_multipleRuns/cis_target_maskDropouts/aggregatedRegulons.json"))

onlyYoungReg <- rjson::fromJSON(file = "../output/ScenicRNA_multipleRuns_young/cis_target_maskDropouts/aggregatedRegulons.json")

onlyYoungRegulons <- names(onlyYoungReg)
onlyOldReg <- rjson::fromJSON(file = "../output/ScenicRNA_multipleRuns_old/cis_target_maskDropouts/aggregatedRegulons.json")
onlyOldRegulons <- names(onlyOldReg)

regulonResultTable <- data.frame(all = as.vector(table(endsWith(allRegulons,'-)'))),
                                 young = as.vector(table(endsWith(onlyYoungRegulons,'-)'))),
                                 old = as.vector(table(endsWith(onlyOldRegulons,'-)'))))

rownames(regulonResultTable) <- c("(+)","(-)")
regulonResultTable
``` 



## settings
```{r}
blank <- grid.rect(gp=gpar(col="white"),draw = F)

colorAge <-  c("#FF8000","#664CFF")

colorTrajStateFinal <- c("#999999","#F0E442","#009E73","#E69F00", "#56B4E9" )


#colorObs <-  c("#490092","#b66dff","#999999","#ffb6db","#009E73", "#F0E442","#E69F00",
#               "#924900","#56B4E9","#0000FF")
#names(colorObs) <- c("iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeu","pMast","pMk","pEr")

colorObs <-  c("#490092","#b66dff","#999999","#ffb6db","#009E73", "#F0E442","#E69F00",
              "#56B4E9","#0000FF")
names(colorObs) <- c("iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr")


tfKrumAdapt <-c("Tal1","Fli1","Gata2","Ikzf1","Spi1","Cebpa","Gata1","Zfpm1","Klf1")

#show_col(colorObs)
```


## New idents for modelling
pNeu and pMast are gathered as pMast succeed to pNeu in pseudotime
```{r}
seurat$Pseudotime <- NA
seurat@meta.data[colnames(monocle),"Pseudotime"] <- pData(monocle)[colnames(monocle),"Pseudotime"]
seurat$State <- NA
seurat@meta.data[colnames(monocle),"State"] <- pData(monocle)[colnames(monocle),"State"]
seurat$observation <- NA
seurat$observation[seurat$Pseudotime < 2 & seurat$phases == "G1/G0"] <- "iHSC"
seurat$observation[seurat$Pseudotime < 2 & seurat$phases == "G2/M"] <- "srHSC"
seurat$observation[seurat$numclust == "tgf"] <- "qHSC"
seurat$observation[seurat$numclust == "ifn"] <- "ifnHSC"
seurat$observation[seurat$numclust == "diff"] <- "preDiff"
seurat$observation[seurat$numclust == "pL1" & seurat$State == 2] <- "pLymph"
seurat$observation[seurat$numclust == "pMk" & seurat$State == 5 ] <- "pMk"
seurat$observation[seurat$numclust == "pEr" & seurat$State == 5 ] <- "pEr"
seurat$observation[seurat$numclust %in% c("pNeu","pMast") & seurat$State == 4 ] <- "pNeuMast"
#seurat$observation[seurat$numclust == "pMast" & seurat$State == 4 ] <- "pMast"



seurat$isObs <- FALSE
seurat$isObs[!is.na(seurat$observation)] <- TRUE

pData(monocle)[colnames(monocle),"observation"] <- seurat@meta.data[colnames(monocle),"observation"] 
pData(monocle)[colnames(monocle),"isObs"] <- seurat@meta.data[colnames(monocle),"isObs"] 

```

##Trajectory plots
```{r, fig.height=3,fig.width=6}
trajPt <- plot_cell_trajectory(monocle,color_by = "Pseudotime",
                               theta = 180,
                               show_branch_points = F,
                               show_tree = F,cell_size = 0.5)  + viridis::scale_color_viridis(option = "D")

trajState <- plot_cell_trajectory(monocle,color_by = "State",
                                  theta = 180,
                                  show_branch_points = F,
                                  show_tree = F,cell_size = 0.5) + 
  scale_color_manual(values = colorTrajStateFinal)+ 
  theme(legend.title = element_blank())+
  guides(colour = guide_legend(override.aes = list(size=3)))

grid.arrange(trajState,blank,trajPt,ncol=3,widths = c(10,1,10))
```

Trajectory observation plots
```{r fig.height =  5, fig.width = 4.5}
monocle$observation <- factor(monocle$observation,levels = names(colorObs))
plot_cell_trajectory(monocle,color_by = "observation",
                     theta = 180,
                     show_branch_points = F,
                     show_tree = F,cell_size = 0.5) + 
  scale_color_manual(values = colorObs,breaks = names(colorObs))+ 
  guides(colour = guide_legend(override.aes = list(size=5),
                               direction = "horizontal")
         ) + 
  theme(legend.title = element_blank(),
       legend.position =  "bottom")
```
```{r  fig.height =  5, fig.width = 4.5}
colorPhases <- c(brewer.pal(9,"RdPu"))[c(3,6,9)]

plot_cell_trajectory(monocle,color_by = "phases",
                     theta = 180,
                     show_branch_points = F,
                     show_tree = F,cell_size = 0.5) + 
  scale_color_manual(values = colorPhases)+ 
  guides(colour = guide_legend(override.aes = list(size=5),
                               direction = "horizontal")
         ) + 
  theme(legend.title = element_blank(),
       legend.position =  "bottom")
```

Keep only cells in defined observations
```{r}
Idents(seurat) <- "observation"
seuratObs <- subset(seurat,ident=names(colorObs))
seuratObs
```


## Find activating regulon Markers of observation
```{r fig.height = 7 , fig.width = 9}
#find cluster regulon markers
Idents(seuratObs) <- "observation"

#Set AUCell slot 
DefaultAssay(seuratObs) <- "AUCell"

observationRegulon <- FindAllMarkers(seuratObs,
                                     only.pos = T,
                                     logfc.threshold= 0,
                                     pseudocount.use = 1,
                                     min.pct = 0.1)

# Compute true mean difference in score because Seurat comput only logFC
# The featureDiff functions is loaded from ../R_src/computeDiffFun.R file

observationRegulon$avg_diff <- NA

for (rm in rownames(observationRegulon)) {
  feature <- observationRegulon[rm,"gene"]
  cells.1 <- colnames(seuratObs)[which(seuratObs$observation == observationRegulon[rm,"cluster"])]
  cells.2 <- colnames(seuratObs)[which(seuratObs$observation != observationRegulon[rm,"cluster"])]
  observationRegulon[rm,"avg_diff"] <- featureDiff(seuratObs,cells.1,cells.2,feature)
}

# cut off on p adjusted value
observationRegulon <- observationRegulon[which(observationRegulon$p_val_adj < 0.001 & observationRegulon$avg_diff > 0.001),]


# rename some columns
colnames(observationRegulon) <- c("p_val","avg_logFC","pct.1","pct.2","p_val_adj","observation","regulon","avg_diff")

# order columns
observationRegulon <- observationRegulon[,c("regulon","observation","avg_diff","p_val_adj","p_val","pct.1","pct.2")]

observationRegulon[observationRegulon$regulon %in% paste0(tfKrumAdapt,"(+)"),]


Idents(seuratObs) <- "observation"



```

##Hierarchical clustering on all activating regulons
Highligth specific TF
```{r,fig.width=6,fig.height=10}
seuratObs@meta.data$observation <- factor(seuratObs@meta.data$observation,levels =c("iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))

Idents(seuratObs) <- "observation"

reg <- rownames(seuratObs)
#reg <- unique(observationRegulon$regulon)
avgClustAucAllRegMark <- AverageExpression(
  seuratObs,
  #seuratObs,
  #slot = "data",
  assays = "AUCell",
  #add.ident = "AGE",
  features =  reg,
  return.seurat = T
)

ord<- hclust( dist(GetAssayData(avgClustAucAllRegMark,slot="scale.data"), 
                   method = "euclidean"),method = "ward.D2")$order

selectedTF <- c("Junb","Egr1","Myc","Klf4","Klf6","Srf",
                "Bclaf1","Tal1",
                "Fli1","Gata2","Ikzf1",
                "Spi1","Cebpa","Gata1",
                "Klf1","Stat1","Irf7","Mef2c")


DoHeatmap(avgClustAucAllRegMark,
          features = reg[ord],
          draw.lines = F,
          group.colors = colorObs) +  
  scale_y_discrete(breaks = c(paste0(selectedTF,"(+)"))) +
  theme(axis.ticks.length.y =unit(.25, "cm"),
        axis.ticks.y = element_line(size = 0.5)) +
  scale_fill_gradientn(colors = c("darkblue","white", "darkred"))


selectedTF <- c("Junb","Egr1","Myc","Klf4","Klf6","Srf",
                "Bclaf1","Tal1",
                "Fli1","Gata2","Zbtb16",
                "Spi1","Cebpa","Gata1",
                "Klf1","Stat1","Irf7","Mef2c")


DoHeatmap(avgClustAucAllRegMark,
          features = reg[ord],
          draw.lines = F,
          group.colors = colorObs
          ) +  
  scale_y_discrete(breaks = c(paste0(selectedTF,"(+)"))) +
  theme(axis.ticks.length.y =unit(.25, "cm"),
        axis.ticks.y = element_line(size = 0.5)) +
  scale_fill_gradientn(colors = c("darkblue","white", "darkred")) 


```
```{r fig.width=6,fig.height=30}
DoHeatmap(avgClustAucAllRegMark,
          features = reg[ord],
          draw.lines = F,
          group.colors = colorObs)+
  scale_fill_gradientn(colors = c("darkblue", "white", "darkred"))
```
## Regulon network analysis

# Analyse complete regulon results in each condition
compute a normalised regulation score on all runs
```{r}
onlyYoungReg <- read.table("../output/regulonAnalysis/youngRegulonTable.tsv")
onlyOldReg <- read.table("../output/regulonAnalysis/oldRegulonTable.tsv")


computeInteractionScore <- function(regTable) {
  colnames(regTable) <-str_split_fixed(colnames(regTable),pattern = "_",n=2)[,1]

  regTable$regScore <- 0
  regTable$regScoreNorm <- 0
  regTable$regRank
  for (t in unique(regTable$gene)) {
    regulators <- regTable[regTable$gene == t,]
    regulators$regScore <- as.numeric(regulators$recoveredTimes) * regulators$importanceMean #NA if auto-reg
    regulators$regScoreNorm <- regulators$regScore / sum(regulators$regScore,na.rm = T) #NA if auto-reg
    regulators$regRank <- rank(-regulators$regScore)
    regTable[rownames(regulators),c("regScore","regScoreNorm","regRank")] <- regulators[rownames(regulators),c("regScore","regScoreNorm","regRank")]

  }
  return(regTable)
}

onlyOldReg <- computeInteractionScore(onlyOldReg)
onlyYoungReg <- computeInteractionScore(onlyYoungReg)


allCellReg <- interactionsTable0[,c(1:7)]

allCellReg <- computeInteractionScore(allCellReg)

allCellReg$regScoreNorm_young <- 0
allCellReg$regScoreNorm_old <- 0
allCellReg[allCellReg$regulon == allCellReg$gene,"regScoreNorm_young"] <- NA
allCellReg[allCellReg$regulon == allCellReg$gene,"regScoreNorm_old"] <- NA


recovRegYoung <- rownames(allCellReg)[rownames(allCellReg) %in%rownames(onlyYoungReg)]
allCellReg[recovRegYoung,"regScoreNorm_young"] <- onlyYoungReg[recovRegYoung,"regScoreNorm"]
allCellReg[recovRegYoung,"recoveredTimes_young"] <- onlyYoungReg[recovRegYoung,"recoveredTimes"]

recovRegOld <- rownames(allCellReg)[rownames(allCellReg) %in%rownames(onlyOldReg)]
allCellReg[recovRegOld,"regScoreNorm_old"] <- onlyOldReg[recovRegOld,"regScoreNorm"]
allCellReg[recovRegOld,"recoveredTimes_old"] <- onlyOldReg[recovRegOld,"recoveredTimes"]

allCellReg$regScoreNormDiff <- allCellReg$regScoreNorm_old - allCellReg$regScoreNorm_young
#allCellReg$regScoreNormRatio <- allCellReg$regScoreNorm_old / allCellReg$regScoreNorm_young

allCellReg <- allCellReg[order(abs(allCellReg$regScoreNormDiff),decreasing = T),]

allCellReg[allCellReg$regulon %in% selectedTF & allCellReg$gene %in% selectedTF,]

interactionsTable0 <- allCellReg

```



## Bone marow cistrome analysis
```{r}
cistromeReg <- read.table("../output/Cistrome_BM/cistromeReg.tsv")
## annotate interactionsTable0 with cistrome analysis result
interactionsTable0$interaction0 <- paste(interactionsTable0$regulon,interactionsTable0$gene,sep = "_")

interactionsTable0$Cistrome_BM <- NA
interactionsTable0[interactionsTable0$regulon  %in% cistromeReg$regulon,"Cistrome_BM"] <- F
interactionsTable0[interactionsTable0$interaction0  %in% cistromeReg$interaction,"Cistrome_BM"] <- T 

print("regulon available in cistrome:")
table(unique(interactionsTable0$regulon )%in% unique(cistromeReg$regulon))
print("scenic interaction found with beta when TF is available:")
table(interactionsTable0$Cistrome_BM)/sum(table(interactionsTable0$Cistrome_BM))

interactionsTable0$nbRecovExp <- NA
interactionsTable0$nbExp <- NA
interactionsTable0$adjustedScore <- NA

interScenicBeta <- unique(interactionsTable0$interaction0)[unique(interactionsTable0$interaction0) %in% unique(cistromeReg$interaction)]

availableTF <- unique(interactionsTable0$regulon)[unique(interactionsTable0$regulon )%in% unique(cistromeReg$regulon)]

for (r in availableTF) {
  interactionsTable0$nbExp[interactionsTable0$regulon == r] <- unique(cistromeReg$nbExp[cistromeReg$regulon == r])
  interactionsTable0$adjustedScore[interactionsTable0$regulon == r] <- 0
  interactionsTable0$nbRecovExp[interactionsTable0$regulon == r] <- 0

}
for (i in interScenicBeta) {
  interactionsTable0[interactionsTable0$interaction0 == i,c("nbRecovExp","adjustedScore")] <- cistromeReg[cistromeReg$interaction== i,c("nbRecovExp","adjustedScore")]
}

```

## Regulon Network analysis

```{r}
#Create node table with top observation for regulon network analysis
observationRegulonTop <- observationRegulon
observationRegulonTop <- observationRegulon[order(observationRegulon$avg_diff,decreasing = T),]

observationRegulonTop <- observationRegulonTop[!duplicated(observationRegulonTop$regulon),]

observationRegulonTop <- observationRegulonTop[order(observationRegulonTop$observation),]

observationRegulonTop$gene <- str_split_fixed(observationRegulonTop$regulon,pattern = "\\(",n=2)[,1]

observationRegulonTop[order(observationRegulonTop$observation,observationRegulonTop$avg_diff,decreasing = c(T,T)),]

```

```{r}
regulonMarker <- str_split_fixed(unique(observationRegulon$regulon),"\\(",n=2)[,1]
regulatorNet <- interactionsTable0[interactionsTable0$gene %in% interactionsTable0$regulon &
                                    interactionsTable0$recoveredTimes >= 45 &
                                    interactionsTable0$regulon %in% regulonMarker &
                                    interactionsTable0$gene %in% regulonMarker 

                                   #interactionsTable$regScoreNorm > 0.1
                                  ,]  
#regulatorNet <- na.exclude(regulatorNet) ## exlude interaction not recovered in all the 3 cell sets
#regulonNetwork <- delete.vertices(degree(regulonNetwork)==0) # remove loops and multiple edges additionally delete isolated nodes
regulatorNet$weight <- regulatorNet$regScoreNorm

regulonNetwork <- graph_from_data_frame(regulatorNet,
                                        directed = TRUE,
                                        vertices = NULL
)
regulonNetwork <- simplify(regulonNetwork,remove.multiple = F,remove.loops = T)


nodeTable <- data.frame(regulon = names(V(regulonNetwork)))
rownames(nodeTable) <- nodeTable$regulon

length(V(regulonNetwork))
length(E(regulonNetwork))
sccRegulonsGraph <- components(regulonNetwork,mode = "strong")


majorScc <- sccRegulonsGraph$membership[which(sccRegulonsGraph$membership == which.max(sccRegulonsGraph$csize))]
set.seed(2021)
regulonNetworkLouvainclustering <- cluster_louvain(as.undirected(regulonNetwork))
nodeTable$community <- NA
for (m in unique(regulonNetworkLouvainclustering$membership)) {
  comNodes <- regulonNetworkLouvainclustering$names[which(regulonNetworkLouvainclustering$membership == m)]
  nodeTable[comNodes,"community"] <- paste0("C_",m)
  print('cluster')
  print(comNodes)
  #plot(subgraph(regulonNetwork,regulonNetworkLouvainclustering$names[which(regulonNetworkLouvainclustering$membership == m)]))
}



nodeTable$observation <- NA
for (o in unique(seuratObs$observation)) {
  observationRegulonTop2 <- observationRegulonTop[observationRegulonTop$gene %in% nodeTable$regulon,]
  nodeObs <- observationRegulonTop2[observationRegulonTop2$observation == o,"gene"]
  nodeTable[nodeObs ,"observation"] <- o
}

# write file for visualisation in cytoscape
write.table(x = regulatorNet,file = "tables/regulatorNet45.tsv",row.names = F,col.names = T,sep = '\t',quote = F)
write.table(x = nodeTable,file = "tables/nodeTable45.tsv",row.names = F,col.names = T,sep = '\t',quote = F)

observationRegulon$gene <- str_split_fixed(observationRegulon$regulon,"\\(",2)[,1]

observationRegulon$community <- NA
for (n in observationRegulon$gene) {
  
observationRegulon[observationRegulon$gene == n,"community"] <- nodeTable[n,"community"]
}

observationRegulon$community <- mapvalues(from = c("C_7","C_2","C_3","C_4","C_5","C_12","C_9","C_1","C_11","C_13","C_10","C_6","C_8"),
                                          to = c(paste0(rep("C",13),c(1:13))),x = observationRegulon$community)

write.table(observationRegulon,"tables/regulonPopulationMarker.tsv",sep = "\t",quote = F,row.names = F)
```

## Some comparison with cistrome
```{r}
print("number of interaction from cistrome beta:")
length(regulatorNet$Cistrome_BM)
print("scenic regulon available in cistrome:")
table(unique(regulatorNet$regulon )%in% unique(cistromeReg$regulon))
table(unique(regulatorNet$regulon )%in% unique(cistromeReg$regulon))/length(unique(regulatorNet$regulon ))
print("scenic interaction found with beta when TF is available in Cistrome:")
table(regulatorNet$Cistrome_BM)/length(regulatorNet$Cistrome_BM[!is.na(regulatorNet$Cistrome_BM)])
```

## Regulon activity of selected TF for constrained trajectory


```{r fig.height=5,fig.width=7}
#selectedTF <- c("Spi1","Cebpa","Zfpm1","Gata1","Klf1","Tal1","Fli1","Gata2","Junc","Egr1","Egr2","Nab2","Irf1")
selectedTF <- c("Egr1","Junb","Bclaf1","Myc","Fli1","Gata2","Spi1","Cebpa","Gata1","Klf1","Tal1","Ikzf1","Zfpm1")
DefaultAssay(seuratObs) <- "AUCell"

selectedTF <- selectedTF[paste0(c(selectedTF),"(+)")%in% rownames(seuratObs)]


seuratObs@meta.data$observation <- factor(seuratObs@meta.data$observation,levels =c("iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))

Idents(seuratObs) <- "observation"


seuratObs2 <- subset(seuratObs,ident = c("ifnHSC"),invert = T)
  






avgClustAuc <- AverageExpression(
  seuratObs2,
  #seuratObs,
  #slot = "data",
  assays = "AUCell",
  features = paste0(c(selectedTF),"(+)"),
  return.seurat = T
)
DoHeatmap(avgClustAuc,features = paste0(selectedTF,"(+)"),group.colors = colorObs,size = 3,draw.line =F )+
  scale_fill_gradientn(colors = c("darkblue", "white", "darkred"))
```

## Discretization with Kmeans
```{r}

# discretizeFeature <- function(avgClust,feature,centers = 2) {
#    set.seed(2020)
#   kmeanRes <- kmeans(GetAssayData(avgClust,slot = "data")[feature,],centers = centers)
#   if (centers == 3) {
#     values <- c(-1,0,1)
#     names(values) <- names(kmeanRes$centers[order(kmeanRes$centers),])
#   } else {
#     values <- c(-1,1)
#     names(values) <- names(kmeanRes$centers[order(kmeanRes$centers),])
#   }
#   disVec <- kmeanRes$cluster                 
#   disVec <- mapvalues(from = names(values),to = values,x = disVec)
#   disVec <- t(as.data.frame(disVec))
#   rownames(disVec) <- feature
#   return(disVec)
# }
# centers = c(3,3,3,3,3,3,3,3,2,2,3,2)
# names(centers) <- rownames(avgClustAuc)
# disKmeansAuc <- discretizeFeature(avgClustAuc,names(centers)[1],centers = centers[1])
# 
# for (t in 2:length(centers)) {
#   disKmeansAuc <- rbind(disKmeansAuc,discretizeFeature(avgClustAuc,names(centers)[t],centers[t]))
# }
# 
# avgClustAuc[["discret"]] <- CreateAssayObject(data=disKmeansAuc)
# 
# DoHeatmap(avgClustAuc,assay = "discret",slot = "data",features = paste0(selectedTF,"(+)"),group.colors = colorObs,size = 3)

```

# discretization with all cells for regulons with more than 10 activated targets


```{r}
discretizeFeatureAllCells <- function(seuratObs2,feature,centers = 2) {
  set.seed(2020)
  kmeanRes <- kmeans(GetAssayData(seuratObs2,slot = "data")[feature,],centers = centers)
  if (centers == 3) {
    values <- c(-1,0,1)
    names(values) <- names(kmeanRes$centers[order(kmeanRes$centers),])
  } else {
    values <- c(-1,1)
    names(values) <- names(kmeanRes$centers[order(kmeanRes$centers),])
  }
  disVec <- kmeanRes$cluster                 
  disVec <- mapvalues(from = names(values),to = values,x = disVec)
  obs <- seurat@meta.data[names(disVec),"observation"]

  resTable <- data.frame(group = disVec,observation = obs)
  resTable2 <- table(resTable)
  disVec <- apply(resTable2, 2, function(x) which.max (x))
  disVec <- mapvalues(from = unique(disVec)[order(unique(disVec))],to = values[c(1:length(unique(disVec)))],x = disVec)


  
  disVec <- t(as.data.frame(disVec))
  rownames(disVec) <- feature

  return(disVec)
}
selectedTF <- c("Egr1","Junb","Bclaf1","Myc","Fli1","Gata2","Spi1","Cebpa","Gata1","Klf1")
selection <- paste0(selectedTF,'(+)')
centers <- rep(2,length(selection))
centers = c(2,2,2, 2, 2, 2, 2, 2, 2, 2)
#centers = c(3,3,3,3,3,3,3,3,3,3,3,3)
names(centers) <- selection
disKmeansAucAll <- discretizeFeatureAllCells(seuratObs2,names(centers)[1],centers = centers[1])

for (t in 2:length(centers)) {
  print(names(centers)[t])
  disKmeansAucAll <- rbind(disKmeansAucAll,discretizeFeatureAllCells(seuratObs2,names(centers)[t],centers[t]))
}

avgClustAuc[["discretAll"]] <- CreateAssayObject(data=disKmeansAucAll)

DoHeatmap(avgClustAuc,assay = "discretAll",slot = "data",features = paste0(selectedTF,"(+)"),group.colors = colorObs,size = 3,draw.lines = F) +
  scale_fill_gradientn(colors = c("darkblue", "grey", "darkred"))

```
```{r}
Idents(seuratObs) <- "SeuratProject"
VlnPlot(seuratObs,features = c("Junb(+)"),pt.size = 0.0001) + NoLegend() +
  geom_hline(yintercept=0.041,color = "red") +
  ylab("AUCell score") +
  xlab("All cells")

```

## RNA average expression

```{r fig.height=4,fig.width=6}
selectedTF <- c("Egr1","Junb","Tal1","Bclaf1","Myc","Fli1","Gata2","Ikzf1","Spi1","Cebpa","Gata1","Klf1","Zfpm1")
CDK46CycDGenes <- c("Ccnd1","Ccnd2","Ccnd3","Cdk4","Cdk6")
CIPKIPGenes  <- c("Cdkn1b","Cdkn1a","Cdkn1c")

cellCycleGenes <- c(CDK46CycDGenes ,CIPKIPGenes)

cellCycleGenes <- cellCycleGenes[cellCycleGenes%in% rownames(seurat)]

avgClustRNA <- AverageExpression(
  seuratObs2,
  #slot = "data",
  assays = "RNA",
  features = c(selectedTF,cellCycleGenes),
  return.seurat = T
)

avgClustRNACC <- data.frame(GetAssayData(avgClustRNA,assay = "RNA",slot = "data"))
CIPKIP <- colSums(avgClustRNACC[CIPKIPGenes[CIPKIPGenes %in% rownames(avgClustRNACC)],])
CDK46CycD <- colSums(avgClustRNACC[CDK46CycDGenes[CDK46CycDGenes %in% rownames(avgClustRNACC)],])
avgClustRNACC <- rbind(avgClustRNACC,CIPKIP=CIPKIP)
avgClustRNACC <- rbind(avgClustRNACC,CDK46CycD=CDK46CycD)
avgClustRNACC <- avgClustRNACC[c(selectedTF,c("CIPKIP","CDK46CycD")),]

avgClustRNACC_seurat <- CreateSeuratObject(counts = avgClustRNACC)
avgClustRNACC_seurat <- ScaleData(avgClustRNACC_seurat)
Idents(avgClustRNACC_seurat) <- colnames(avgClustRNACC_seurat)


DoHeatmap(avgClustRNACC_seurat,
          features = c(selectedTF,c("Zfpm1","CDK46CycD","CIPKIP")),
          group.colors = colorObs,
          size = 3,
          draw.lines = FALSE)+
  scale_fill_gradientn(colors = c("darkblue", "white", "darkred"))
```

## Discretization of RNA levels for genes and regulons =< 10 activated targets

```{r}
selection <- c("Tal1","Ikzf1","Zfpm1",cellCycleGenes)

avgClustRNA <- AverageExpression(
  seuratObs2,
  #slot = "data",
  assays = "RNA",
  features = selection,
  return.seurat = T
)


discretizeFeature <- function(avgClust,feature,centers = 2,removeZero =F) {
  set.seed(2020)
  kmeanRes <- kmeans(GetAssayData(avgClust,slot = "data")[feature,],centers = centers)
  if (centers == 3) {
    values <- c(-1,0,1)
    names(values) <- names(kmeanRes$centers[order(kmeanRes$centers),])
  } else {
    values <- c(-1,1)
    names(values) <- names(kmeanRes$centers[order(kmeanRes$centers),])
  }
  disVec <- kmeanRes$cluster                 
  disVec <- mapvalues(from = names(values),to = values,x = disVec)
  disVec <- t(as.data.frame(disVec))
  rownames(disVec) <- feature
  return(disVec)
}
centers <- rep(3,length(selection))
#centers = c(2,3,2,2,2,2,2,2,2,2)
#centers = c(2,3,3,3,3,2,3,3,2,2,3,2,2,2,3)
#centers = c(3,3,3,3,3,3,3,3,3,3,3,3,2,2,2)
names(centers) <- rownames(avgClustRNA)
disKmeansRNA <- discretizeFeature(avgClustRNA,names(centers)[1],centers = centers[1])

for (t in 2:length(centers)) {
  disKmeansRNA <- rbind(disKmeansRNA,discretizeFeature(avgClustRNA,names(centers)[t],centers[t]))
}

avgClustRNA[["discret"]] <- CreateAssayObject(data=disKmeansRNA)

DoHeatmap(avgClustRNA,
          assay = "discret",
          slot = "data",
          features = selection,
          group.colors = colorObs,
          size = 3,draw.lines = FALSE)+
  scale_fill_gradientn(colors = c("darkblue", "grey", "darkred"))

```
# Sum discretization for cell cycle gene complexes
```{r, fig.height=5,fig.width=5}
disMatrix <- rbind(disKmeansAucAll[,colnames(disKmeansRNA)],disKmeansRNA[c("Tal1","Ikzf1","Zfpm1"),])

CDK46CycD <- colSums(disKmeansRNA[CDK46CycDGenes,])
CDK46CycD[CDK46CycD > 1] <- 1
CDK46CycD[CDK46CycD < 1] <- -1

CIPKIP <- colSums(disKmeansRNA[CIPKIPGenes,])
CIPKIP[CIPKIP > 1] <- 1
CIPKIP[CIPKIP < 1] <- -1

disMatrix <- rbind(disMatrix,CDK46CycD,CIPKIP)

colnames(disMatrix)[colnames(disMatrix) == "qHSC"] <- "qHSC"

df2 <- melt(disMatrix[rev(rownames(disMatrix)),])
ggplot(df2) +
  geom_tile( aes(x=Var2 , y=Var1, fill= as.factor(value) )) +
  scale_fill_manual(guide=FALSE, values=c("darkblue", "grey","darkred")) +
  scale_x_discrete(guide = guide_axis(angle = 45)) 

disMatrixBonesis <- disMatrix
disMatrixBonesis[disMatrixBonesis == 0] <- ""

disMatrixBonesis[disMatrixBonesis == -1] <- "0"
disMatrixBonesis[disMatrixBonesis == 1] <- "1"


rownames(disMatrixBonesis) <- str_split_fixed(rownames(disMatrixBonesis),pattern = "\\(",n=2)[,1]
write.csv(t(disMatrixBonesis),"../output/Inference/obsDataDis.csv",quote = F) 


```

## Some plot on influence graph

```{r, fig.height= 4,fig.width=4}
infGraphTable <- read.table("../output/Inference/influenceGraph/infGraphTable45.tsv",sep = '\t',header = T)

interactionCistromeIg <- rownames(infGraphTable[(!is.na(infGraphTable$cistromeAdjScore) & infGraphTable$cistromeAdjScore >0),])
interactionRefIg <- rownames(infGraphTable[!is.na(infGraphTable$ref),])
interactionScenicIg <- rownames(infGraphTable[infGraphTable$Scenic,])



ggVennDiagram(list(Scenic= interactionScenicIg,
          Reference = interactionRefIg,
          cistrome = interactionCistromeIg), 
          label_alpha = 0)

```



## Save for next step (figure 3)
```{r}
saveRDS(seuratObs,"seuratObs.rds")
write.table(interactionsTable0,"tables/interactionTable.tsv",sep ="\t",quote = F,row.names = F)
```

