---
title: "figures"
author: "Herault"
date: "19/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## env
```{r cars}
suppressMessages(library(ggplot2))
suppressMessages(library(spatstat))
suppressMessages(library(Seurat))
suppressMessages(library(monocle))
#suppressMessages(library(BoolNet))
suppressMessages(library(dplyr))
suppressMessages(library(igraph))
suppressMessages(library(plyr))
suppressMessages(library(stringr))
suppressMessages(library(grid))
suppressMessages(library(gridExtra))
suppressMessages(library(RColorBrewer))
#suppressMessages(library(gProfileR))
suppressMessages(library(gplots))
suppressMessages(library(reshape2))
suppressMessages(library(ggpmisc))
suppressMessages(library(ggthemes))

if (!requireNamespace("ggVennDiagram", quietly = TRUE))
  install.packages("ggVennDiagram",repos='http://cran.us.r-project.org')

suppressMessages(library("ggVennDiagram"))



library("readxl")
source("../R_src/computeDiffFun.R")
source("../R_src/Enrichment.R")
source("../R_src/getSigPerCells.R")
source("../R_src/funForSeurat.R")
source("../R_src/funForPlots.R")



```

## load results

```{r pressure, echo=FALSE}
interactionsTable0 <- read.table("../output/regulonAnalysis/mainRegulonTable.tsv") 
tfTested <- read.table("../output/publicData/mm_mgi_tfs.txt")
tfSelected <- read.table("../input/selectedTF.txt")
#seurat <- readRDS("../../herault_et_al/scHSC_herault/report/seurat_report.rds")
seuratObs <- readRDS("seuratObs.rds")
monocle <- readRDS("../../herault_et_al/scHSC_herault/report/monocle_report.rds")

# Loading regulon score table
interactionsTable0 <- read.table("tables/interactionTable.tsv",header = T,sep = "\t")


```

## settings
```{r}
blank <- grid.rect(gp=gpar(col="white"),draw = F)

colorAge <-  c("#FF8000","#664CFF")

colorTrajStateFinal <- c("#999999","#F0E442","#009E73","#E69F00", "#56B4E9" )


#colorObs <-  c("#490092","#b66dff","#999999","#ffb6db","#009E73", "#F0E442","#E69F00",
#               "#924900","#56B4E9","#0000FF")
#names(colorObs) <- c("iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeu","pMast","pMk","pEr")

colorObs <-  c("#490092","#b66dff","#999999","#ffb6db","#009E73", "#F0E442","#E69F00",
              "#56B4E9","#0000FF")
names(colorObs) <- c("iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr")

```



## Table for retained interactions for influence graph

Add normalised grnboost2 importance score.

```{r}
interactionTableSolution <- read.csv("tables/interactionTableFinalSol.csv",row.names = 1)
selectedTF <- c("Junb","Egr1","Myc","Bclaf1","Tal1","Fli1","Gata2","Ikzf1","Spi1","Cebpa","Gata1","Klf1","Zfpm1")
CDK46CycDGenes <- c("Ccnd1","Ccnd2","Ccnd3",'Cdk4','Cdk6')
CIPKIPGenes <- c("Cdkn1a","Cdkn1b","Cdkn1c")
influenceGraphScenic <-interactionsTable0[(interactionsTable0$gene %in% c(selectedTF,CDK46CycDGenes,CIPKIPGenes)) &
                     (interactionsTable0$regulon %in% c(selectedTF,CDK46CycDGenes,CIPKIPGenes)),]

influenceGraphScenic$nodeModel <- influenceGraphScenic$gene
influenceGraphScenic$nodeModel[influenceGraphScenic$gene %in% CDK46CycDGenes] <- "CDK46CycD"
influenceGraphScenic$nodeModel[influenceGraphScenic$gene %in% CIPKIPGenes] <- "CIPKIP"

influenceGraphScenic$interactionModel <- paste(influenceGraphScenic$regulon,influenceGraphScenic$nodeModel,influenceGraphScenic$mor,sep = "_")


rownames(interactionTableSolution) <- paste(interactionTableSolution$tf,interactionTableSolution$target,sep = "_",interactionTableSolution$mor)

interactionTableSolutionScenic <- influenceGraphScenic[influenceGraphScenic$interactionModel %in% rownames(interactionTableSolution),]
#write.table(interactionTableSolutionScenic,"tables/interactionRegulonTableFinalSol.tsv",sep = '\t',quote = F, row.names = F)
#write.table(interactionTableSolution,"tables/interactionFinalSol.tsv",sep = '\t',quote = F, row.names = F)
```

```{r}
infGraphTable <- read.table("../output/Inference/influenceGraph/infGraphTable45.tsv",sep = '\t',header = T)
infGraphTable$solution <- FALSE
rownames(infGraphTable) <- paste0(infGraphTable$interaction0,"_",infGraphTable$mor)
infGraphTable[rownames(interactionTableSolution),"solution"] <- T

infGraphTable <- infGraphTable[order(infGraphTable$solution,decreasing = T),colnames(infGraphTable)[-11]]


influenceGraphScenic$solution <- F

influenceGraphScenic[influenceGraphScenic$interactionModel %in% rownames(interactionTableSolution),"solution"] <- T

influenceGraphScenic <- influenceGraphScenic[order(influenceGraphScenic$solution,decreasing = T),c("regulon","gene","mor","recoveredTimes","recoveredTimes_young","recoveredTimes_old","regScoreNorm","regScoreNorm_young","regScoreNorm_old","regScoreNormDiff","adjustedScore","solution")]

write.table(infGraphTable,"tables/influenceGraphWithSolution.tsv",sep = '\t',quote = F, row.names = F)
write.table(influenceGraphScenic,"tables/influenceGraphWithSolutionRegulon.tsv",sep = '\t',quote = F, row.names = F)
```



## Aging Perturbation


### Global heatmap with age split Hierarchical clustering on all activating regulons
Highligth specific TF
```{r,fig.width=8,fig.height=10}
seuratObs@meta.data$observation <- factor(seuratObs@meta.data$observation,levels =c("iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))

Idents(seuratObs) <- "observation"

reg <- rownames(seuratObs)
#reg <- unique(observationRegulon$regulon)
avgClustAucAllRegMark <- AverageExpression(
  seuratObs,
  #seuratObs,
  #slot = "data",
  assays = "AUCell",
  #add.ident = "AGE",
  features =  reg,
  return.seurat = T
)

ord<- hclust( dist(GetAssayData(avgClustAucAllRegMark,slot="scale.data"), 
                   method = "euclidean"),method = "ward.D2")$order


reg <- rownames(seuratObs)
#reg <- unique(observationRegulon$regulon)
avgClustAucAllRegMark <- AverageExpression(
  seuratObs,
  #seuratObs,
  #slot = "data",
  assays = "AUCell",
  add.ident = "AGE",
  features =  reg,
  return.seurat = T
)

avgClustAucAllRegMark@meta.data$AGE <- str_split_fixed(rownames(avgClustAucAllRegMark@meta.data),pattern = "_",n=2)[,2]
avgClustAucAllRegMark@meta.data$observation <- factor(avgClustAucAllRegMark@meta.data$orig.ident,names(colorObs))
#ord<- hclust( dist(GetAssayData(avgClustAucAllRegMark,slot="scale.data"), 
#                   method = "euclidean"),method = "ward.D2")$order


selectedTF <- c("Junb","Egr1","Myc","Klf4","Klf6","Srf",
                "Bclaf1","Tal1",
                "Fli1","Gata2","Ikzf1",
                "Spi1","Cebpa","Gata1",
                "Klf1","Stat1","Irf7","Mef2c")


DoHeatmap(avgClustAucAllRegMark,
          features = reg[ord],
          draw.lines = T,
          lines.width = 1,
          group.colors = colorObs) +  
  scale_y_discrete(breaks = c(paste0(selectedTF,"(+)"))) +
  theme(axis.ticks.length.y =unit(.25, "cm"),
        axis.ticks.y = element_line(size = 0.5))+
  scale_fill_gradientn(colors = c("darkblue","white", "darkred"),na.value = "white") 


selectedTF <- c("Junb","Egr1","Myc","Klf4","Klf6","Srf",
                "Bclaf1","Tal1",
                "Fli1","Gata2","Zbtb16",
                "Spi1","Cebpa","Gata1",
                "Klf1","Stat1","Irf7","Mef2c")



selectedTF <- c("Egr1","Klf4","Klf6","Atf3","Atf4",
                "Rel","Nfkb1",
                "Jun","Fos","Junb",
                "Spi1","Myc","Runx3","Sox3",
                "Cebpb","Cebpe",
                "Fli1","Mef2c")

selectedTF <- c("Klf4","Klf6","Klf4","Atf3",
                "Rel","Nfkb1","Rela","Relb",
                "Fos","Jun",
                "Spi1","Myc","Runx3","Sox4",
                "Cebpb",
                "Mef2c")

DoHeatmap(avgClustAucAllRegMark,
          features = reg[ord],
          draw.lines = T,
          lines.width = 1,
          group.colors = colorObs) +  
  scale_y_discrete(breaks = c(paste0(selectedTF,"(+)"))) +
  theme(axis.ticks.length.y =unit(.25, "cm"),
        axis.ticks.y = element_line(size = 0.5)) +
  scale_fill_gradientn(colors = c("darkblue","white", "darkred"),na.value = "white") 



  
```

### Solution analysis

```{r, fig.height= 4,fig.width=4}
interactionCistrome <- rownames(interactionTableSolution[(!is.na(interactionTableSolution$cistromeAdjScore) & interactionTableSolution$cistromeAdjScore >0),])
interactionRef <- rownames(interactionTableSolution[interactionTableSolution$ref != "",])
interactionScenic <- rownames(interactionTableSolution[interactionTableSolution$Scenic != "False",])



#library(venneuler)

ggVennDiagram(list(Scenic= interactionScenic,
          Reference = interactionRef,
          cistrome = interactionCistrome), 
          label_alpha = 0)


```


### Regulon activities markers of aging

### aging marker test

```{r}
seuratObs$platform <- str_split_fixed(seuratObs$sampleName,"_",2)[,2]
source("../R_src/computeDiffFun.R")
agingRegulonPerObs<- lapply(names(colorObs),
                            FindAgingMarkers4,
                            seuratObs,
                            identCol = "observation",
                            test.use = "wilcox",
                            keepDiverging= T,
                            logfc.threshold = 0,
                            pseudocount.use = 1,
                            min.pct = 0.1,
                            filterOnPadj = F)

FindAgingMarkers4(hspc.combined = seuratObs,identCol = "observation",
                            test.use = "wilcox",
                            keepDiverging= T,
                            logfc.threshold = 0,
                            pseudocount.use = 1,
                            min.pct = 0.1,
                            filterOnPadj = F,cluster = "iHSC")


agingRegulonPerObsTable <- agingRegulonPerObs[[1]]
for (s in c(2:length(agingRegulonPerObs))) {
  agingRegulonPerObsTable <- rbind(agingRegulonPerObsTable,agingRegulonPerObs[[s]])
}
# 
# seuratObs$cluster.AGE <- paste(seuratObs@meta.data[,"observation"],
#                                      seuratObs@meta.data[,"AGE"], sep = "_")
# Idents(object = seuratObs) <- "cluster.AGE"
# 
#   
# 
# test <- FindConservedMarkers(seuratObs,
#                              assay = DefaultAssay(seuratObs),
#                              grouping.var = "platform",
#                              test.use="wilcox",
#                              ident.1 = paste0("iHSC","_Aged"),
#                              ident.2 = paste0("iHSC","_Young"),
#                              pseudocount.use = 1,
#                              min.pct = 0.1,
#                              logfc.threshold = 0
# )


dim(agingRegulonPerObsTable)

agingRegulonPerObsTable$State <- str_split_fixed(agingRegulonPerObsTable$Cluster,pattern = "_",n=3)[,1]

colnames(agingRegulonPerObsTable)[which(colnames(agingRegulonPerObsTable)=="State")] <- "observation"


agingRegulonPerObsTable <- getTrueDiff(seuratObs[,which(seuratObs$platform == "A")],
                                       agingRegulonPerObsTable,
                                       colIdent = "observation",
                                       suffix = "A")

agingRegulonPerObsTable <- getTrueDiff(seuratObs[,which(seuratObs$platform == "B")],
                                       agingRegulonPerObsTable,
                                       colIdent = "observation",
                                       suffix = "B")


agingRegulonPerObsTable$min_avg_diff <- apply(agingRegulonPerObsTable[,c("avg_diff_A","avg_diff_B")], 1, FUN=getExtAvgDiff) 


dim(agingRegulonPerObsTable)

#Exclude AUCell score differences with an opposite sign of variation (pval set to NA by FindAgingMarkers)
agingRegulonPerObsTable <- na.exclude(agingRegulonPerObsTable)

dim(agingRegulonPerObsTable)

#Exclude AUCell score differences with a combined pval < 0.05
agingRegulonPerObsTable <- agingRegulonPerObsTable[which(agingRegulonPerObsTable$minimump_p_val < 0.001),]

dim(agingRegulonPerObsTable)

colnames(agingRegulonPerObsTable)[which(colnames(agingRegulonPerObsTable) == "Cluster")] <- "group"
colnames(agingRegulonPerObsTable)[which(colnames(agingRegulonPerObsTable) == "Gene")] <- "regulon"



agingRegulonPerObsTable <- agingRegulonPerObsTable[,c("regulon","observation","group","minimump_p_val","max_pval","min_avg_diff","A_p_val","avg_diff_A","A_pct.1","A_pct.2","B_p_val","avg_diff_B","B_pct.1","B_pct.2")]




# Filter on average differences before writing final table
agingRegulonPerObsTable <- agingRegulonPerObsTable[which(abs(agingRegulonPerObsTable$min_avg_diff) > 0.001),]

# regulonTestTable <- list(stateRegulon = observationRegulon,
#                          agingRegulonPerObs = agingRegulonPerObsTable)

#WriteXLS(x =regulonTestTable,"paperTables/regulonTable.xlsx",row.names = F)

write.table(agingRegulonPerObsTable,"tables/regulonPopulationAgingMarker.tsv",sep = "\t",quote = F,row.names = F)
```
```{r fig.width=3,fig.height=2} 

data <- ddply(agingRegulonPerObsTable,~observation + sign(min_avg_diff),nrow)
colnames(data) <- c("observation","sign","count")

data$sens <- "Up"
data$sens[data$sign == -1] <- "Down"

data$observation <- factor(data$observation,levels = rev(names(colorObs)))
ggplot(data = data,aes(y=count,fill=observation,x = sens,width=.75)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values = rev(colorObs))


```


```{r}
selectedTF <- unique(interactionTableSolution$tf)
agingRegulonModel <- agingRegulonPerObsTable[agingRegulonPerObsTable$regulon %in% paste0(selectedTF,"(+)"),]
unique(agingRegulonModel$regulon)
agingRegulonModel[order(abs(agingRegulonModel$min_avg_diff),decreasing = T),]
agingRegulonModel[order(agingRegulonModel$regulon,decreasing = T),]

```

```{r, fig.height=7,fig.width=7.5}
VlnPlot(seuratObs, unique(agingRegulonModel$regulon),split.by = "AGE",ncol = 3,pt.size = 0,split.plot = T,cols = rev(colorAge),idents = c( c("iHSC","srHSC","qHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))) 

```
```{r fig.height=5,fig.width=5}

VlnPlot(seuratObs, c("Egr1(+)","Junb(+)","Fli1(+)","Spi1(+)"),
        split.by = "AGE",ncol = 2,pt.size = 0,split.plot = T,
        cols = rev(colorAge),idents = c( c("iHSC","srHSC","qHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))
        ) 

```


```{r}
agingRegulonModelInitial <- agingRegulonModel[agingRegulonModel$observation == "iHSC",]
agingRegulonModelInitial[order(abs(agingRegulonModelInitial$min_avg_diff),decreasing = T),]

```
```{r}
agingRegulonModelInitial <- agingRegulonModel[agingRegulonModel$observation == "qHSC",]
agingRegulonModelInitial[order(abs(agingRegulonModelInitial$min_avg_diff),decreasing = T),]
```
```{r}
agingRegulonModelInitial <- agingRegulonModel[agingRegulonModel$observation == "preDiff",]
agingRegulonModelInitial[order(abs(agingRegulonModelInitial$min_avg_diff),decreasing = T),]
```

## model gene alterations
```{r,fig.height=5,fig.width=5}
VlnPlot(seuratObs,c("Cdkn1a","Cdkn1c","Cdkn1b"),split.by = "AGE",assay = "RNA",pt.size = 0,ncol = 2)
```


### Interaction score 

Venn of interaction between TF in the different scenic processing
```{r}
onlyYoungReg <- read.table("../output/regulonAnalysis/youngRegulonTable.tsv")
onlyOldReg <- read.table("../output/regulonAnalysis/oldRegulonTable.tsv")

youngInt <- onlyYoungReg[onlyYoungReg$gene %in% tfTested$V1,"interaction"]
agedInt <- onlyOldReg[onlyOldReg$gene %in% tfTested$V1,"interaction"]
allInt <- interactionsTable0[interactionsTable0$gene %in% tfTested$V1,"interaction"]

ggVennDiagram(list(all= allInt,
          aged = agedInt,
          young = youngInt))

ggVennDiagram(list(all= allInt,
          aged = agedInt[agedInt %in% allInt],
          young = youngInt[youngInt %in% allInt]))


```
```{r}
selectedTF <- c("Egr1","Junb","Bclaf1","Myc","Fli1","Gata2","Spi1","Cebpa","Gata1","Klf1","Tal1","Ikzf1","Zfpm1")
CDK46CycDGenes <- c("Ccnd1","Ccnd2","Ccnd3","Cdk4","Cdk6")
CIPKIPGenes  <- c("Cdkn1b","Cdkn1a","Cdkn1c")

cellCycleGenes <- c(CDK46CycDGenes ,CIPKIPGenes)
modelGenes <- c(selectedTF,CIPKIPGenes,cellCycleGenes)

youngInt <- onlyYoungReg[onlyYoungReg$gene %in% modelGenes & onlyYoungReg$regulon %in% modelGenes,"interaction"]
agedInt <- onlyOldReg[onlyOldReg$gene %in% modelGenes & onlyOldReg$regulon %in% modelGenes,"interaction"]
allInt <- interactionsTable0[interactionsTable0$gene %in% modelGenes & interactionsTable0$regulon %in% modelGenes,"interaction"]

ggVennDiagram(list(all= allInt,
          aged = agedInt,
          young = youngInt))

```


```{r fig.height=4,fig.width=4}


regScoreNormDiffData <- na.exclude(interactionTableSolutionScenic[abs(interactionTableSolutionScenic$regScoreNormDiff) > 0.10,c("interaction","regScoreNorm","regScoreNorm_young","regScoreNorm_old","regScoreNormDiff")])
regScoreNormDiffData$AGE <- "Aged"
regScoreNormDiffData$AGE[regScoreNormDiffData$regScoreNormDiff<0] <- "Young"

regScoreNormDiffData$interaction <- factor(regScoreNormDiffData$interaction,levels = rev(regScoreNormDiffData$interaction))
ggplot(regScoreNormDiffData,aes(x = interaction,y=regScoreNormDiff,fill = AGE)) + geom_bar(stat="identity") + 
  coord_flip() +
  scale_fill_manual(values = colorAge)
```


```{r}
hist(abs(interactionsTable0$regScoreNormDiff[interactionsTable0$gene %in% tfTested$V1]),breaks = 20,
     main = "Histogram of NIS differences with aging",
     xlab = "Normalised interaction score (NIS) differences between TFs with aging")

table(abs(na.exclude(interactionsTable0[interactionsTable0$gene %in% tfTested$V1,"regScoreNormDiff"]))>0.4)/length(na.exclude(interactionsTable0[interactionsTable0$gene %in% tfTested$V1,"regScoreNormDiff"]))
```

```{r fig.height=2,fig.width=3.5}
rownames(regScoreNormDiffData) <- str_split_fixed(regScoreNormDiffData$interaction,"_1",2)[,1] # there are only activation
rownames(regScoreNormDiffData) <- gsub(rownames(regScoreNormDiffData),pattern = "_",replacement = "->")
regScoreNormDiffData$interaction <- rownames(regScoreNormDiffData)

CebpaReg <- melt(regScoreNormDiffData[c("Spi1->Cebpa","Gata2->Cebpa"),c("interaction","regScoreNorm_old","regScoreNorm_young","regScoreNorm")])
CebpaReg$interaction <- factor(CebpaReg$interaction,levels = c("Spi1->Cebpa","Gata2->Cebpa"))
CebpaReg$model <- NA
CebpaReg$model[CebpaReg$variable == "regScoreNorm"] <- "global"
CebpaReg$model[CebpaReg$variable == "regScoreNorm_young"] <- "young"
CebpaReg$model[CebpaReg$variable == "regScoreNorm_old"] <- "old"

CebpaReg$model <- factor(CebpaReg$model,levels = c("young","old","global"))
ggplot(CebpaReg,
       aes(y=value,x = interaction,fill = model)) + 
  geom_bar(stat="identity", position =position_dodge()) + 
  ylab(label = "Score") +
  coord_flip() + 
  scale_fill_manual(values = c(colorAge,"grey")) 
```




## Variation in attractor proportion with aging

```{r}

seurat <- readRDS("../../herault_et_al/scHSC_herault/report/seurat_report.rds")
seurat@meta.data$observation <- "others"
seurat@meta.data[rownames(seuratObs@meta.data),"observation"] <- as.character(seuratObs@meta.data[,"observation"])
seurat$observation <- factor(seurat$observation,
                              levels = c("others","iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))

clusterAge <- ddply(seurat@meta.data,~observation + AGE,nrow)
#clusterAge$observation <- factor(paste("  ",clusterAge$observation,sep = ""),
#                              levels = paste("  ",levels(seurat$observation),sep = ""))

clusterAge$observation <- factor(clusterAge$observation,
                              levels = c("others","iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))

propExpect <- table(seurat@meta.data$AGE)/length(seurat@meta.data$AGE)[]
propYoungExp <- propExpect[[unique(seurat@meta.data$AGE)[1]]]

clusterAge$AGE <- factor(clusterAge$AGE , levels = c("Aged","Young")) 


age <- ggplot(data.frame(clusterAge), aes(fill = AGE,y = V1, x=observation,levels = "Young","Aged")) +
  geom_bar( stat="identity", position="fill")+
  scale_fill_manual( values= rev(colorAge))+
  scale_y_continuous(name = "Age (%)", labels = c(0,25,50,75,100))+
  ylab(label = "")+xlab(label = "") + 
  coord_flip() + 
  geom_hline(yintercept = propYoungExp)+
  theme(legend.title=element_blank()) + 
  labs(fill = "age:")+
  scale_fill_manual(values = colorAge)+ 
  scale_y_continuous( labels = c("0%","25%","50%","75%","100%"))

ageEnrich <- getEnrichAge(seurat,clustCol ="observation",metaCol = "AGE") 

ageEnrich <- as.data.frame(t(ageEnrich))
ageEnrich$color <- "black"
ageEnrich[which(as.numeric(as.vector(ageEnrich$phyper)) < 0.05 & ageEnrich$enrich == "Young"),"color"] <- colorAge[1]
ageEnrich[which(as.numeric(as.vector(ageEnrich$phyper)) < 0.05 & ageEnrich$enrich == "Aged"),"color"] <-colorAge[2]

legendBoxSize = 5

age <- age + 
  theme(axis.text.y = element_text(colour = ageEnrich[,'color'])) +
  scale_fill_discrete(breaks=c("Young","Old")) +
  scale_fill_manual( values= rev(colorAge))+
  guides(colour = guide_legend(override.aes = list(size=legendBoxSize)))

#adding barplot count

clusterCount <- ggplot(data.frame(clusterAge), aes(y = log10(V1), x=observation)) +
  theme(axis.title.y = element_blank(),axis.text.y = element_blank()) +
  geom_bar(stat = "identity") + 
  ylab(label = "log10(Cell number)") +
  coord_flip() 

grid2bClust <- arrangeGrob(ggplotGrob(age+ NoLegend() ),
                           ggplotGrob(clusterCount),
                           g_legend(age,"vertical"),
                           widths = c(3,1.5,0.5))

grid.arrange(grid2bClust)


```
```{r fig.width=3,fig.height=1.5}
bp <- list()
for (o in clusterAge$observation) {

bp[[o]] <-  ggplot(data.frame(clusterAge[clusterAge$observation == o,]), aes(fill = AGE,y = V1, x=observation)) +
  geom_bar( stat="identity", position="fill")+
  scale_fill_manual( values= rev(colorAge))+
  scale_y_continuous(name = "Age (%)", labels = c(0,25,50,75,100))+
  ylab(label = "")+xlab(label = "") + 
  coord_flip() + 
  geom_hline(yintercept = propYoungExp,size = 1)+
  theme(legend.title=element_blank()) + 
  labs(fill = "age:")+
  scale_fill_manual(values = rev(colorAge))+ 
  facet_wrap(~ observation)  +
  scale_y_continuous( labels = c("0%","25%","50%","75%","100%")) + theme_void() + NoLegend()
}
  
grid.arrange(bp$iHSC,bp$pLymph,bp$pNeuMast,bp$qHSC,bp$preDiff, bp$pEr,bp$srHSC,bp$ifnHSC,bp$pMk,ncol=3)

```



```{r}
# 
# seuratObs2 <- subset(seuratObs,ident= "ifnHSC",invert = T)
# clusterAge <- ddply(seuratObs2@meta.data,~observation + AGE,nrow)
# #clusterAge$observation <- factor(paste("  ",clusterAge$observation,sep = ""),
# #                              levels = paste("  ",levels(seuratObs2$observation),sep = ""))
# 
# clusterAge$observation <- factor(clusterAge$observation,
#                               levels = c("others","iHSC","srHSC","qHSC","ifnHSC","preDiff","pLymph","pNeuMast","pMk","pEr"))
# 
# propExpect <- table(seuratObs2@meta.data$AGE)/length(seuratObs2@meta.data$AGE)[]
# propYoungExp <- propExpect[[unique(seuratObs2@meta.data$AGE)[1]]]
# 
# clusterAge$AGE <- factor(clusterAge$AGE , levels = c("Aged","Young")) 
# 
# 
# age <- ggplot(data.frame(clusterAge), aes(fill = AGE,y = V1, x=observation,levels = "Young","Aged")) +
#   geom_bar( stat="identity", position="fill")+
#   scale_fill_manual( values= rev(colorAge))+
#   scale_y_continuous(name = "Age (%)", labels = c(0,25,50,75,100))+
#   ylab(label = "")+xlab(label = "") + 
#   coord_flip() + 
#   geom_hline(yintercept = propYoungExp)+
#   theme(legend.title=element_blank()) + 
#   labs(fill = "age:")+
#   scale_fill_manual(values = colorAge)+ 
#   scale_y_continuous( labels = c("0%","25%","50%","75%","100%"))
# 
# ageEnrich <- getEnrichAge(seuratObs2,clustCol ="observation",metaCol = "AGE") 
# 
# ageEnrich <- as.data.frame(t(ageEnrich))
# ageEnrich$color <- "black"
# ageEnrich[which(as.numeric(as.vector(ageEnrich$phyper)) < 0.05 & ageEnrich$enrich == "Young"),"color"] <- colorAge[1]
# ageEnrich[which(as.numeric(as.vector(ageEnrich$phyper)) < 0.05 & ageEnrich$enrich == "Aged"),"color"] <-colorAge[2]
# 
# legendBoxSize = 5
# 
# age <- age + 
#   theme(axis.text.y = element_text(colour = ageEnrich[,'color'])) +
#   scale_fill_discrete(breaks=c("Young","Old")) +
#   scale_fill_manual( values= rev(colorAge))+
#   guides(colour = guide_legend(override.aes = list(size=legendBoxSize)))
# 
# #adding barplot count
# 
# clusterCount <- ggplot(data.frame(clusterAge), aes(y = log10(V1), x=observation)) +
#   theme(axis.title.y = element_blank(),axis.text.y = element_blank()) +
#   geom_bar(stat = "identity") + 
#   ylab(label = "log10(Cell number)") +
#   coord_flip() 
# 
# grid2bClust <- arrangeGrob(ggplotGrob(age+ NoLegend() ),
#                            ggplotGrob(clusterCount),
#                            g_legend(age,"vertical"),
#                            widths = c(3,1.5,0.5))
# 
# grid.arrange(grid2bClust)

```

```{r fig.width=3.5,fig.height=2}
# attractors <- subset(seuratObs,ident = c("pEr","pMk","pNeuMast","pLymph"))
# clusterAge <- ddply(attractors@meta.data,~observation + AGE,nrow)
# clusterAge$observation <- factor(paste("  ",clusterAge$observation,sep = ""),
#                               levels = paste("  ",levels(attractors$observation),sep = ""))
# 
# propExpect <- table(attractors@meta.data$AGE)/length(attractors@meta.data$AGE)[]
# propYoungExp <- propExpect[[unique(attractors@meta.data$AGE)[1]]]
# 
# clusterAge$AGE <- factor(clusterAge$AGE , levels = c("Aged","Young")) 
seurat@meta.data$observation <- "nonPrimed"
seurat@meta.data[rownames(seuratObs@meta.data),"observation"] <- as.character(seuratObs@meta.data[,"observation"])
seurat@meta.data$observation[!seurat@meta.data$observation %in% c("pEr","pLymph","pMk","pNeuMast","preDiff")] <- "nonPrimed"

seurat$observation <- factor(seurat$observation,
                              levels = c("nonPrimed","pLymph","pNeuMast","pMk","pEr","preDiff"))

clusterAge <- ddply(seurat@meta.data,~observation + AGE,nrow)
#clusterAge$observation <- factor(paste("  ",clusterAge$observation,sep = ""),
#                              levels = paste("  ",levels(seurat$observation),sep = ""))

clusterAge$observation <- factor(clusterAge$observation,
                              levels = c("nonPrimed","pLymph","pNeuMast","pMk","pEr","preDiff"))

propExpect <- table(seurat@meta.data$AGE)/length(seurat@meta.data$AGE)[]
propYoungExp <- propExpect[[unique(seurat@meta.data$AGE)[1]]]

clusterAge$AGE <- factor(clusterAge$AGE , levels = c("Aged","Young")) 


bp <- list()
for (o in clusterAge$observation) {

bp[[o]] <-  ggplot(data.frame(clusterAge[clusterAge$observation == o,]), aes(fill = AGE,y = V1, x=observation)) +
  geom_bar( stat="identity", position="fill")+
  scale_fill_manual( values= rev(colorAge))+
  scale_y_continuous(name = "Age (%)", labels = c(0,25,50,75,100))+
  ylab(label = "")+xlab(label = "") + 
  coord_flip() + 
  geom_hline(yintercept = propYoungExp)+
  theme(legend.title=element_blank()) + 
  labs(fill = "age:")+
  scale_fill_manual(values = rev(colorAge))+ 
  facet_wrap(~ observation)  +
  scale_y_continuous( labels = c("0%","25%","50%","75%","100%")) + theme_void() + NoLegend()
}
  
grid.arrange(blank,bp$pLymph,bp$pNeuMast,bp$nonPrimed,bp$preDiff, bp$pEr,blank,blank,bp$pMk,ncol=3)
```


## Link to pathways
```{r}
# selectedTF <- c("Egr1","Junb","Myc","Gata2","Spi1","Bclaf1","Cebpa","Tal1","Ikzf1","Fli1","Klf1","Zfpm1",CDK46CycDGenes,CIPKIPGenes)
# #write.table(selectedTF,"../input/selectedTF.txt",sep = "\t")
# library(progeny)
# prgData <- get("model_mouse_full", envir = .GlobalEnv)
# prgData <- prgData[order(prgData$pathway,prgData$p.value,decreasing = c(T,F)),]
# prgData[prgData$gene %in% selectedTF & prgData$p.value < 0.05 & abs(prgData$weight) > 2,]

```




