---
title: "Report_scRNA_infer"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading env

```{r loading, echo=FALSE}
suppressMessages(library(ggplot2))
suppressMessages(library(Seurat))
suppressMessages(library(monocle))
#suppressMessages(library(BoolNet))
suppressMessages(library(dplyr))
suppressMessages(library(igraph))
suppressMessages(library(plyr))
suppressMessages(library(stringr))
suppressMessages(library(grid))
suppressMessages(library(gridExtra))
suppressMessages(library(RColorBrewer))

dir.create("images",showWarnings = F)
dir.create("tables",showWarnings = F)
```

## Loading Bonzanni boolean network

```{r}
bonzanni <- read.table("../publicData/Bonzanni_2013.reggraph",sep = " ",stringsAsFactors  = F)
colnames(bonzanni) <- c("tf","mor","target")
bonzanni$mor[which(bonzanni$mor == "-|")] <- -1
bonzanni$mor[which(bonzanni$mor == "->")] <- 1



for (r in rownames(bonzanni)) {
  if(bonzanni[r,"mor"] == "-?") {
    #print(bonzanni[r,])
    neg <- bonzanni[r,] 
    neg$mor <- -1
    bonzanni[r,"mor"] <- 1
    bonzanni <- rbind(bonzanni,neg)
  }
}

bonzanni$interaction <- paste(bonzanni$tf,
                              bonzanni$target,
                              bonzanni$mor,sep ="_")
#show bonznni network tf


graphBonzanniOri <- graph_from_data_frame(bonzanni[c(1,3,2)], directed = TRUE, vertices = NULL)
edgesOri <- bonzanni[,"mor"]
edge.color.ori <- rep("blue",length(edgesOri))
edge.color.ori[which(edgesOri == -1)] <- "red"

bonzanni_adja <- as_adjacency_matrix(graph = graphBonzanniOri)



```


## Loading Krumsiek adapted boolean network

```{r}
KrumAdapt <- read.table("../output/Modelling/MatchingDataStateNet.reggraph",sep = " ",stringsAsFactors  = F)
colnames(KrumAdapt) <- c("tf","mor","target")
KrumAdapt$mor[which(KrumAdapt$mor == "-|")] <- -1
KrumAdapt$mor[which(KrumAdapt$mor == "->")] <- 1



for (r in rownames(KrumAdapt)) {
  if(KrumAdapt[r,"mor"] == "-?") {
    #print(KrumAdapt[r,])
    neg <- KrumAdapt[r,] 
    neg$mor <- -1
    KrumAdapt[r,"mor"] <- 1
    KrumAdapt <- rbind(KrumAdapt,neg)
  }
}

KrumAdapt$interaction <- paste(KrumAdapt$tf,
                              KrumAdapt$target,
                              KrumAdapt$mor,sep ="_")
#show bonznni network tf


graphKrumAdaptOri <- graph_from_data_frame(KrumAdapt[c(1,3,2)], directed = TRUE, vertices = NULL)
edgesOri <- KrumAdapt[,"mor"]
edge.color.ori <- rep("blue",length(edgesOri))
edge.color.ori[which(edgesOri == -1)] <- "red"

KrumAdapt_adja <- as_adjacency_matrix(graph = graphKrumAdaptOri)



```


## Backgournd tf

```{r}
tf_mouse <- read.table("../output/publicData/mm_mgi_tfs.txt")
length(tf_mouse$V1)

tf_tested <- tf_mouse$V1
```
## Scenic network from rna data

TO DO add dorothea tf in the possible targets. And in the input of Scenic?

```{r scenicRnaNet,  fig.height=15,fig.width=14}

scenicNetRna <- read.csv("../output/ScenicRNA/tf_grn_regulons.csv") #TO DO add dorothea tf in the possible targets
scenicNetRna$mor <- NA
scenicNetRna$mor[which(scenicNetRna$interaction == "+")] <- "1"
scenicNetRna$mor[which(scenicNetRna$interaction == "-")] <- "-1"
scenicNetRna <- scenicNetRna[,c("TF","Target","mor")]
colnames(scenicNetRna) <- c("tf","target","mor")
for (r in rownames(bonzanni)) {
  if(bonzanni[r,"mor"] == "-?") {
    #print(bonzanni[r,])
    neg <- bonzanni[r,] 
    neg$mor <- -1
    bonzanni[r,"mor"] <- 1
    bonzanni <- rbind(bonzanni,neg)
  }
}

scenicNetRna$interaction <- paste(scenicNetRna$tf,
                                            scenicNetRna$target,
                                            scenicNetRna$mor,sep ="_")




scenicNetRnaGraph <- graph_from_data_frame(scenicNetRna, directed = TRUE, vertices = NULL)


# some stats
table(scenicNetRna$mor)
length(E(scenicNetRnaGraph))
length(V(scenicNetRnaGraph))
edge_density(scenicNetRnaGraph, loops = TRUE)



#compare with bonznni network tf
scenicNetRnaBonza <- scenicNetRna[which(scenicNetRna$tf %in% colnames(bonzanni_adja) & scenicNetRna$target %in% colnames(bonzanni_adja)),c("tf","target","mor")]

inner_join(scenicNetRnaBonza,bonzanni)

#
scenicNetRnaBonzaGraph <- graph_from_data_frame(scenicNetRnaBonza, directed = TRUE, vertices = NULL)

edges.rna <- scenicNetRnaBonza[,"mor"]
edge.color.rna <- rep("blue",length(edges.rna))
edge.color.rna[which(edges.rna == -1)] <- "red"

scenicRnaInterBonza <- inner_join(scenicNetRnaBonza,bonzanni)

scenicRnaGraphBonzanniShared <- graph_from_data_frame(scenicRnaInterBonza,directed = TRUE, vertices = NULL)


edgesShared.rna <- scenicRnaInterBonza[,"mor"]
edgesShared.color.rna <- rep("blue",length(edgesShared.rna))
edgesShared.color.rna[which(edgesShared.rna == -1)] <- "red"

par(mfrow=c(2,2))
plot(scenicNetRnaBonzaGraph, 
     edge.color = edge.color.rna,
     main="Influence graph bonzanni  TFs\nScenic RNA regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)
plot(graphBonzanniOri,
     edge.color = edge.color.ori,
     main="Influence graph bonzanni",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)
plot(scenicRnaGraphBonzanniShared,
     edge.color = edgesShared.color.rna,
     main="Influence graph bonzanni\nrecovered in Scenic RNA regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)

```
## Significance of the enrichment in Bonzanni interaction for the Scenic RNA regulons
Take all the mouse TF took as input in the workflow for background.

```{r}
#source("../../herault_et_al/scHSC_herault/R_src/Enrichment.R")


interactionMarked <- scenicNetRna$interaction[which(scenicNetRna$interaction %in% bonzanni$interaction)] 

#tf_tested <- unique(tf_dorothea_ABC$tf)
backgroundInteraction <- 2*(length(tf_tested)*(length(tf_tested)+1))/2 #complete graph plus self loop by two (inhibiton and activation)

phyper(q=length(interactionMarked) -1, 
       m=length(bonzanni$interaction),                 
       n=backgroundInteraction - length(bonzanni$interaction), k= length(scenicNetRna$interaction), lower.tail=FALSE)

length(which(endsWith(interactionMarked,suffix = "_1")))/length(which(endsWith(bonzanni$interaction,"_1")))
length(which(endsWith(interactionMarked,suffix = "_-1")))/length(which(endsWith(bonzanni$interaction,"_-1")))

```

## Scenic network from rna data mask dropouts option

TO DO add dorothea tf in the possible targets. And in the input of Scenic?

```{r scenicRnaNet,  fig.height=15,fig.width=14}

scenicNetRnaMaskDrop <- read.csv("../output/ScenicRNA/tf_grn_regulons_maskDropouts.csv") #TO DO add dorothea tf in the possible targets
scenicNetRnaMaskDrop$mor <- NA
scenicNetRnaMaskDrop$mor[which(scenicNetRnaMaskDrop$interaction == "+")] <- "1"
scenicNetRnaMaskDrop$mor[which(scenicNetRnaMaskDrop$interaction == "-")] <- "-1"
scenicNetRnaMaskDrop <- scenicNetRnaMaskDrop[,c("TF","Target","mor")]
colnames(scenicNetRnaMaskDrop) <- c("tf","target","mor")
scenicNetRnaMaskDrop$interaction <- paste(scenicNetRnaMaskDrop$tf,
                                            scenicNetRnaMaskDrop$target,
                                            scenicNetRnaMaskDrop$mor,sep ="_")


scenicNetRnaMaskDropGraph <- graph_from_data_frame(scenicNetRnaMaskDrop, directed = TRUE, vertices = NULL)


# some stats
table(scenicNetRnaMaskDrop$mor)
length(E(scenicNetRnaMaskDropGraph))
length(V(scenicNetRnaMaskDropGraph))
edge_density(scenicNetRnaMaskDropGraph, loops = TRUE)



#compare with bonznni network tf
scenicNetRnaMaskDropBonza <- scenicNetRnaMaskDrop[which(scenicNetRnaMaskDrop$tf %in% colnames(bonzanni_adja) & scenicNetRnaMaskDrop$target %in% colnames(bonzanni_adja)),c("tf","target","mor")]

inner_join(scenicNetRnaMaskDropBonza,bonzanni)

#
scenicNetRnaMaskDropBonzaGraph <- graph_from_data_frame(scenicNetRnaMaskDropBonza, directed = TRUE, vertices = NULL)

edges.rna <- scenicNetRnaMaskDropBonza[,"mor"]
edge.color.rna <- rep("blue",length(edges.rna))
edge.color.rna[which(edges.rna == -1)] <- "red"

scenicRnaMaskDropInterBonza <- inner_join(scenicNetRnaMaskDropBonza,bonzanni)

scenicRnaMaskDropGraphBonzanniShared <- graph_from_data_frame(scenicRnaMaskDropInterBonza,directed = TRUE, vertices = NULL)


edgesShared.rnaMaskDrop <- scenicRnaMaskDropInterBonza[,"mor"]
edgesShared.color.rnaMaskDrop <- rep("blue",length(edgesShared.rnaMaskDrop))
edgesShared.color.rnaMaskDrop[which(edgesShared.rnaMaskDrop == -1)] <- "red"

par(mfrow=c(2,2))
plot(scenicNetRnaMaskDropBonzaGraph, 
     edge.color = edge.color.rna,
     main="Influence graph bonzanni  TFs\nScenic RNA regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)
plot(graphBonzanniOri,
     edge.color = edge.color.ori,
     main="Influence graph bonzanni",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)
plot(scenicRnaMaskDropGraphBonzanniShared,
     edge.color = edgesShared.color.rnaMaskDrop,
     main="Influence graph bonzanni\nrecovered in Scenic RNA regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)

```

```{r, fig.height=15,fig.width=14}

#compare with krumAdpa network tf
scenicNetRnaMaskDropKrumAdapt <- scenicNetRnaMaskDrop[which(scenicNetRnaMaskDrop$tf %in% colnames(KrumAdapt_adja) & scenicNetRnaMaskDrop$target %in% colnames(KrumAdapt_adja)),c("tf","target","mor")]

inner_join(scenicNetRnaMaskDropKrumAdapt,KrumAdapt)

#
scenicNetRnaMaskDropKrumAdaptGraph <- graph_from_data_frame(scenicNetRnaMaskDropKrumAdapt, directed = TRUE, vertices = NULL)

edges.rna <- scenicNetRnaMaskDropKrumAdapt[,"mor"]
edge.color.rna <- rep("blue",length(edges.rna))
edge.color.rna[which(edges.rna == -1)] <- "red"

scenicRnaMaskDropInterKrumAdapt <- inner_join(scenicNetRnaMaskDropKrumAdapt,KrumAdapt)

scenicRnaMaskDropGraphKrumAdaptShared <- graph_from_data_frame(scenicRnaMaskDropInterKrumAdapt,directed = TRUE, vertices = NULL)


edgesShared.rnaMaskDrop <- scenicRnaMaskDropInterKrumAdapt[,"mor"]
edgesShared.color.rnaMaskDrop <- rep("blue",length(edgesShared.rnaMaskDrop))
edgesShared.color.rnaMaskDrop[which(edgesShared.rnaMaskDrop == -1)] <- "red"

par(mfrow=c(2,2))
plot(scenicNetRnaMaskDropKrumAdaptGraph, 
     edge.color = edge.color.rna,
     main="Influence graph KrumAdapt  TFs\nScenic RNA regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)
plot(graphKrumAdaptOri,
     edge.color = edge.color.ori,
     main="Influence graph KrumAdapt",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)
plot(scenicRnaMaskDropGraphKrumAdaptShared,
     edge.color = edgesShared.color.rnaMaskDrop,
     main="Influence graph KrumAdapt\nrecovered in Scenic RNA regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
vertex.label.cex = 1.5)
```







## Significance of the enrichment in Bonzanni interaction for the Scenic RNA regulons
Take all the mouse TF took as input in the workflow for background.

```{r}
#source("../../herault_et_al/scHSC_herault/R_src/Enrichment.R")


interactionMarkedMaskDrop <- scenicNetRnaMaskDrop$interaction[which(scenicNetRnaMaskDrop$interaction %in% bonzanni$interaction)] 

#tf_tested <- unique(tf_dorothea_ABC$tf)
#backgroundInteraction <- 2*(length(tf_tested)*(length(tf_tested)+1))/2 #complete graph plus self loop by two (inhibiton and activation)

phyper(q=length(interactionMarkedMaskDrop) -1, 
       m=length(bonzanni$interaction),                 
       n=backgroundInteraction - length(bonzanni$interaction), k= length(scenicNetRnaMaskDrop$interaction), lower.tail=FALSE)

length(which(endsWith(interactionMarkedMaskDrop,suffix = "_1")))/length(which(endsWith(bonzanni$interaction,"_1")))

length(which(endsWith(interactionMarkedMaskDrop,suffix = "_-1")))/length(which(endsWith(bonzanni$interaction,"_-1")))

```
## Significance of the enrichment in Bonzanni interaction for the Scenic RNA regulons
Take all the mouse TF took as input in the workflow for background.

```{r}
#source("../../herault_et_al/scHSC_herault/R_src/Enrichment.R")


interactionMarkedMaskDrop <- scenicNetRnaMaskDrop$interaction[which(scenicNetRnaMaskDrop$interaction %in% KrumAdapt$interaction)] 

#tf_tested <- unique(tf_dorothea_ABC$tf)
#backgroundInteraction <- 2*(length(tf_tested)*(length(tf_tested)+1))/2 #complete graph plus self loop by two (inhibiton and activation)

phyper(q=length(interactionMarkedMaskDrop) -1, 
       m=length(KrumAdapt$interaction),                 
       n=backgroundInteraction - length(KrumAdapt$interaction), k= length(scenicNetRnaMaskDrop$interaction), lower.tail=FALSE)

length(which(endsWith(interactionMarkedMaskDrop,suffix = "_1")))/length(which(endsWith(KrumAdapt$interaction,"_1")))

length(which(endsWith(interactionMarkedMaskDrop,suffix = "_-1")))/length(which(endsWith(KrumAdapt$interaction,"_-1")))

```





given the better result of mask dropout option we decide to continue with this scenic results for the building of influence graph and the search of constraints.

Loading of seurat and monocle results:
```{r}
seurat <- readRDS("../../herault_et_al/scHSC_herault/report/seurat_report.rds")
monocle <- readRDS("../../herault_et_al/scHSC_herault/report/monocle_report.rds")
```

## View selected TF in violins
```{r, fig.height=7,fig.width=14}
DefaultAssay(seurat) <- "RNA"
Idents(seurat) <- "numclust"
selectedTF <- c("Dnmt3a","E2f","Rb1","Trp53","Tet2","Sp1","Sp3","Itga6")

Fzd <- rownames(seurat)[which(startsWith(rownames(seurat),prefix = "Fzd"))]


selectedTF <- c("Dnmt3a","Rb1","Tet2","Sp1","Ociad1","Uhrf1")


VlnPlot(seurat,features = selectedTF,pt.size = 0.1,split.by = "AGE")
VlnPlot(seurat,features = selectedTF,pt.size = 0.1)

```

## Add the scenic results in new assays

For scenic on RNA with mask dropouts options

```{r}

regulonsTableRNA <- read.csv("../output/ScenicRNA/AUCell_maskDropouts/regulons_enrichment.csv",check.names = F) 
rownames(regulonsTableRNA) <- gsub(x = regulonsTableRNA[,1],pattern = "\\.",replacement = "-")
# Exclude pB cells to plot regulons in Traj without pB cells
regulonsTableRNA <- regulonsTableRNA[colnames(seurat),-1]


seurat[["AUCellRNA"]] <- CreateAssayObject(data=t(as.matrix(regulonsTableRNA)))
```

## find TF markers of trajectory section to define constaints


```{r}
colorAnnot <- c(brewer.pal(12,"Paired"))

getTerminalCells <- function(cds) {
  tip_leaves <- names(which(igraph::degree(minSpanningTree(cds)) ==
                              1))
  tip_leaves <- sub(x = tip_leaves, pattern = "Y_", replacement = "")
  print("tip_leaves : ")
  print(tip_leaves)
  pData(cds)$terminalCells <- cds@auxOrderingData$DDRTree$pr_graph_cell_proj_closest_vertex %in%
    tip_leaves
  return(cds)
}

monocle <- getTerminalCells(monocle)

plot_cell_trajectory(monocle, color_by = "terminalCells")

pData(monocle)$Section <- paste(pData(monocle)$State,pData(monocle)$terminalCells,sep ="_")
pData(monocle)$Section <- factor(pData(monocle)$Section,levels = c("1_TRUE","1_FALSE",
                                                                   "2_TRUE","2_FALSE",
                                                                   "3_TRUE","3_FALSE",
                                                                   "4_TRUE","4_FALSE",
                                                                   "5_TRUE","5_FALSE"))

pData(monocle)$Section <- mapvalues(from =  c("1_TRUE","1_FALSE",
                                              "2_TRUE","2_FALSE",
                                              "3_TRUE","3_FALSE",
                                              "4_TRUE","4_FALSE",
                                              "5_TRUE","5_FALSE"),
                                    to =  c("1_Start","1",
                                            "2_End","2",
                                            "3_End","3",
                                            "4_End","4",
                                            "5_End","5"),
                                    x= pData(monocle)$Section)

colorSections <- c("grey40","#999999",
                   "#E69F00","#FFFF99",
                   "#56B4E9",
                   colorAnnot[c(8,7)],
                   colorAnnot[c(2,1)])


plot_cell_trajectory(monocle, color_by = "Section",theta = 180,show_branch_points = F) + scale_color_manual(values = colorSections)
```

## Transfert to Seurat object and test for tf markers using the different slot
```{r}

# Add monocle results to a seurat combined object
seuratOrdered <- subset(seurat, idents = "pB",invert = TRUE)

seuratOrdered$Pseudotime <- pData(monocle)[rownames(seuratOrdered@meta.data),"Pseudotime"]
seuratOrdered$State <- pData(monocle)[rownames(seuratOrdered@meta.data),"State"]
seuratOrdered$Section <- pData(monocle)[rownames(seuratOrdered@meta.data),"Section"]
```

# find section TF markers on RNA data
```{r}
Idents(seuratOrdered) <- "Section"
DefaultAssay(seuratOrdered) <- "RNA"


section1MarkersRNA <- FindAllMarkers(seuratOrdered,
                               only.pos = T,
                               logfc.threshold = 0.25,
                               min.pct =0.1,
                               slot = "data")

# Cut off on p adjusted value
section1MarkersRNA <- section1MarkersRNA[which(section1MarkersRNA$p_val_adj < 0.05),]

section1TfRNA <- section1MarkersRNA[which(section1MarkersRNA$gene %in% tf_tested),]

length(unique(section1TfRNA$gene))

#section1TfTopRNA <- section1MarkersRNA[which(section1MarkersRNA$avg_logFC> 0.25),]

dupRNA <- section1TfRNA[which(duplicated(section1TfRNA$gene,fromLast = FALSE) |duplicated(section1TfRNA$gene,fromLast = TRUE )),]

dupRNA[order(rownames(dupRNA)),]

uniRNA <- section1TfRNA[which(section1TfRNA$gene %in% dupRNA$gene == F),]

length(unique(uniRNA$gene))

```
## Same with scenic aucell RNA score (with mask dropouts option at ctx step)
```{r}

#Test states differences
Idents(seuratOrdered) <- "Section"

#Set AUCell slot 
DefaultAssay(seuratOrdered) <- "AUCellRNA"


sectionScenicRegRNA <- FindAllMarkers(seuratOrdered,
                               only.pos = T,
                               logfc.threshold= 0,
                               pseudocount.use = 1,
                               min.pct = 0.1)

# Compute true mean difference in score because Seurat comput only logFC
# The featureDiff functions is loaded from ../R_src/computeDiffFun.R file

sectionScenicRegRNA$avg_diff <- NA
sectionScenicRegRNA$cluster <- factor(sectionScenicRegRNA$cluster,levels = levels(seuratOrdered$Section ))

source("../../herault_et_al/scHSC_herault/R_src/computeDiffFun.R")

for (rm in rownames(sectionScenicRegRNA)) {
  feature <- sectionScenicRegRNA[rm,"gene"]
  cells.1 <- colnames(seuratOrdered)[which(seuratOrdered$Section == sectionScenicRegRNA[rm,"cluster"])]
  cells.2 <- colnames(seuratOrdered)[which(seuratOrdered$Section != sectionScenicRegRNA[rm,"cluster"])]
  sectionScenicRegRNA[rm,"avg_diff"] <- featureDiff(seuratOrdered,cells.1,cells.2,feature)
}

sectionScenicRegActRNA <-sectionScenicRegRNA[which(endsWith(sectionScenicRegRNA$gene,suffix = "+)")),]
sectionScenicRegInhRNA <-sectionScenicRegRNA[which(endsWith(sectionScenicRegRNA$gene,suffix = "-)")),]


# cut off on p adjusted value
sectionScenicRegActRNA <- sectionScenicRegActRNA[which(sectionScenicRegActRNA$p_val_adj < 0.05 & sectionScenicRegActRNA$avg_diff > 0.0025),]
dim(sectionScenicRegActRNA)
length(unique(sectionScenicRegActRNA$gene))


sectionScenicRegInhRNA <- sectionScenicRegInhRNA[which(sectionScenicRegInhRNA$p_val_adj < 0.05 & sectionScenicRegInhRNA$avg_diff > 0.0025),]
dim(sectionScenicRegInhRNA)
length(unique(sectionScenicRegInhRNA$gene))


## Look at correspondance with Tf markers in RNA

sectionScenicRegActRNA$gene <- str_split_fixed(sectionScenicRegActRNA$gene,pattern = "\\(",n=2)[,1]

tfRnaAct <- inner_join(section1TfRNA[,c("cluster","gene")],sectionScenicRegActRNA[,c("cluster","gene")])



sectionScenicRegInhRNA$gene <- str_split_fixed(sectionScenicRegInhRNA$gene,pattern = "\\(",n=2)[,1]

tfRnaInh <- inner_join(section1TfRNA[,c("cluster","gene")],sectionScenicRegInhRNA[,c("cluster","gene")])

tfKept <- inner_join(tfRnaAct[,c("cluster","gene")],tfRnaInh[,c("cluster","gene")])

```

```{r}
ActKept <- sectionScenicRegActRNA[which(sectionScenicRegActRNA$p_val_adj < 0.05 & sectionScenicRegActRNA$avg_diff > 0.003),]

length(unique(ActKept$gene))

tfRnaAct2 <- inner_join(section1TfRNA[which(section1TfRNA$p_val_adj < 0.05 & section1TfRNA$avg_logFC > 0.25),c("cluster","gene")],
                        sectionScenicRegActRNA[which(sectionScenicRegActRNA$p_val_adj < 0.05 & sectionScenicRegActRNA$avg_logFC > 0.003),c("cluster","gene")])

#Find Tf for starting point only on AUCell 
Act <- sectionScenicRegActRNA[which(sectionScenicRegActRNA$p_val_adj < 0.05 & sectionScenicRegActRNA$avg_diff > 0.0025),]

Act_1_Start <- Act[which(Act$cluster == "1_Start"),]

Act_2_End <- Act[which(Act$cluster == "2_End"),]

Act_5_End <- Act[which(Act$cluster == "5_End"),]



```
Find some possible constraint by merging 3,4,4_end,5,5_end ; 1 and 1_start ; 2,2_end
```{r}

```

Proposal for ASP input

```{r}
influenceGraphTable <- rbind(bonzanni[,c("tf","target","mor")],scenicNetRnaMaskDrop[,c("tf","target","mor")]) 

influenceGraphTable <- influenceGraphTable[which(influenceGraphTable$tf %in% tfRnaAct2$gene),]
influenceGraphTable <- influenceGraphTable[which(influenceGraphTable$target %in% tfRnaAct2$gene),]


dim(influenceGraphTable)
dim(unique(influenceGraphTable))

influenceGraphTable <- unique(influenceGraphTable)

influenceGraph <- graph_from_data_frame(d =influenceGraphTable[,c("tf","target","mor")], directed = TRUE, vertices = NULL)

length(E(influenceGraph))
length(V(influenceGraph))
table(influenceGraphTable$mor)


edgesInfluenceGraph <- influenceGraphTable[,"mor"]
edgesInfluenceGraph.color <- rep("blue",length(edgesInfluenceGraph))
edgesInfluenceGraph.color[which(edgesInfluenceGraph == -1)] <- "red"

plot(influenceGraph, 
     edge.color = edgesInfluenceGraph.color,
     main="Influence graph bonzanni  TFs\nall Dorothea regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
     vertex.label.cex = 1.5)


```
Minimal ASP input, selected determinant TF

```{r,fig.height=10}
# selectedTF <- tfRnaAct$gene[tfRnaAct$gene %in% colnames(bonzanni_adja)]
# selectedTF
# selectedTF <- c("Fli1","Erg","Gata2","Fos","Junb","Jun","Jund","Myb","Sox4","Irf8","Cebpe","Cebpa","E2f1","Trim28","Ybx1")

#selectedTF <- unique(c("Fli1","Erg","Gata2","Fos","Junb","Jun","Jund","Myb","Sox4","Irf8","Cebpe","Cebpa","E2f1","Gata1","Ybx1","Zfpm1","Myc","Ezh2"))

selectedTF <- c("Gata2","Runx1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Ikzf1","Myc","Junb","Erg","Egr1","Myb","Hoxb4","Gfi1")

influenceGraphTableMin <- scenicNetRnaMaskDrop[,c("tf","target","mor")]

influenceGraphTableMinTemp <- influenceGraphTableMin[which(influenceGraphTableMin$tf %in% tfRnaAct2$gene &influenceGraphTableMin$target %in% tfRnaAct2$gene),]

influenceGraphTableMin <- influenceGraphTableMin[which(influenceGraphTableMin$tf %in% selectedTF),]
influenceGraphTableMin <- influenceGraphTableMin[which(influenceGraphTableMin$target %in% selectedTF),]


dim(influenceGraphTableMin)
dim(unique(influenceGraphTableMin))

influenceGraphTableMin <- unique(influenceGraphTableMin)

influenceGraphMin <- graph_from_data_frame(d =influenceGraphTableMin[,c("tf","target","mor")], directed = TRUE, vertices = NULL)

length(E(influenceGraphMin))
length(V(influenceGraphMin))
table(influenceGraphMin$mor)


edgesInfluenceGraphMin <- influenceGraphTableMin[,"mor"]
edgesInfluenceGraphMin.color <- rep("blue",length(edgesInfluenceGraphMin))
edgesInfluenceGraphMin.color[which(edgesInfluenceGraphMin == -1)] <- "red"

plot(influenceGraphMin, 
     edge.color = edgesInfluenceGraphMin.color,
     main="Influence graph bonzanni  TFs\nall Dorothea regulons",
     vertex.size =30,
     vertex.shape = "rectangle",
     vertex.label.cex = 1.5,
     layout=layout.circle)

selectedTF <- c("Gata2","Runx1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Ikzf1","Myc","Junb","Erg","Egr1","Myb")





hspc.combined.selectedTF <- ScaleData(seurat,features =paste0(c(selectedTF),"(+)"))




mapal <- colorRampPalette(RColorBrewer::brewer.pal(11,"RdBu"))(256)

DefaultAssay(seurat) <- "AUCellRNA"

paste0(c(selectedTF),"(+)") %in% rownames(seurat)

selectedTF_neg <- paste0(c(selectedTF),"(-)")[which(paste0(c(selectedTF),"(-)") %in% rownames(seurat))]


test <- AverageExpression(
  seurat,
  slot = "data",
  features = paste0(c(selectedTF),"(+)"),
  return.seurat = T
)

test2 <- AverageExpression(
  seurat,
  add.ident = "AGE",
  slot = "data",
  features = paste0(c(selectedTF),"(+)"),
  return.seurat = T
)




test_neg <- AverageExpression(
  seurat,
  slot = "data",
  features = selectedTF_neg,
  return.seurat = T
)

test2_neg <- AverageExpression(
  seurat,
  add.ident = "AGE",
  slot = "data",
  features =selectedTF_neg,
  return.seurat = T
)

test@meta.data[,c("AGE","priming")] <- seurat@meta.data[,c("AGE","priming")]
test@meta.data$numclust <- colnames(test)
test2@meta.data[,c("AGE","priming")] <- seurat@meta.data[,c("AGE","priming")]
test2@meta.data$numclust <- str_split_fixed(colnames(test2),"_",n=2)[,1]



test_neg@meta.data[,c("AGE","priming")] <- seurat@meta.data[,c("AGE","priming")]
test_neg@meta.data$numclust <- colnames(test_neg)
test2@meta.data[,c("AGE","priming")] <- seurat@meta.data[,c("AGE","priming")]
test2_neg@meta.data$numclust <- str_split_fixed(colnames(test2_neg),"_",n=2)[,1]

Idents(test_neg) <- "numclust"
Idents(test2_neg) <- "numclust"
DoHeatmap(test_neg,features = selectedTF_neg)
DoHeatmap(test2_neg,features = selectedTF_neg)

Idents(test) <- "numclust"
Idents(test2) <- "numclust"
DoHeatmap(test,features = paste0(c(selectedTF),"(+)"))
DoHeatmap(test2,features = paste0(c(selectedTF),"(+)"))


DefaultAssay(seurat) <- "RNA"
Idents(seurat) <- "numclust"


test_gene<- AverageExpression(
  seurat,
  slot = "data",
  features = selectedTF,
  return.seurat = T
)

test2_gene <- AverageExpression(
  seurat,
  add.ident = "AGE",
  slot = "data",
  features =selectedTF,
  return.seurat = T
)

Idents(test_gene) <- "numclust"
Idents(test2_gene) <- "numclust"
DoHeatmap(test_gene,features = selectedTF)
DoHeatmap(test2_gene,features = selectedTF)


# DoHeatmap(hspc.combined.selectedTF,features = paste0(c(selectedTF),"(+)"),group.by = "numclust",slot = "scale.data",
#           cells = colnames(hspc.combined.selectedTF)[which(hspc.combined.selectedTF$priming == "primed")]) +   scale_fill_gradientn(colours = rev(mapal))
# 
# 
# DoHeatmap(hspc.combined.selectedTF,features = paste0(c(selectedTF),"(+)"),group.by = "numclust",slot = "scale.data",
#           cells = colnames(hspc.combined.selectedTF)[which(hspc.combined.selectedTF$priming == "non primed")]) +   scale_fill_gradientn(colours = rev(mapal))


GetAssayData(test,slot = "scale.data")
```

```{r}
DefaultAssay(seurat) <- "RNA"
VlnPlot(seurat,"Zfpm1",split.by = "AGE")
```

Same with bonzanni interactions added

```{r fig.height=10}
influenceGraphTable <- rbind(bonzanni[,c("tf","target","mor")],scenicNetRna[,c("tf","target","mor")]) 
influenceGraphTable <- unique(influenceGraphTable)
influenceGraphTableMinTemp <- influenceGraphTableMin[which(influenceGraphTableMin$tf %in% tfRnaAct2$gene &influenceGraphTableMin$target %in% tfRnaAct2$gene),]


influenceGraphTable <- influenceGraphTable[which(influenceGraphTable$tf %in% selectedTF),]
influenceGraphTable <- influenceGraphTable[which(influenceGraphTable$target %in% selectedTF),]


dim(influenceGraphTable)
dim(unique(influenceGraphTable))

influenceGraphTable <- unique(influenceGraphTable)

influenceGraph <- graph_from_data_frame(d =influenceGraphTable[,c("tf","target","mor")], directed = TRUE, vertices = NULL)

length(E(influenceGraph))
length(V(influenceGraph))
table(influenceGraph$mor)


edgesinfluenceGraph <- influenceGraphTable[,"mor"]
edgesinfluenceGraph.color <- rep("blue",length(edgesinfluenceGraph))
edgesinfluenceGraph.color[which(edgesinfluenceGraph == -1)] <- "red"

plot(influenceGraph, 
     edge.color = edgesinfluenceGraph.color,
     main="Influence graph Bonzanni and marker TFs",
     vertex.size =30,
     vertex.shape = "rectangle",
     vertex.label.cex = 1.5,
     layout=layout.circle)
```



Table for constraints
```{r}
ActKept[which(ActKept$gene %in% selectedTF),c("cluster","gene")] 
tfRnaAct2[which(tfRnaAct2$gene %in% selectedTF),]

unique(ActKept$gene[which(ActKept$gene %in% selectedTF)])
```
## TF selected not targeted in scenic interaction
```{r}
influenceGraphTableMin[which((influenceGraphTableMin$tf %in% unique(influenceGraphTableMin$target) == F)),]
```



## View selected TF in violins
```{r, fig.height=14,fig.width=15}
DefaultAssay(seuratOrdered) <- "RNA"
selectedTF <- c("Gata2","Zfpm1","Ikzf1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Egr1","Junb","Dnmt3a","Tet2")
VlnPlot(seuratOrdered,features = selectedTF,pt.size = 0.1)

seurat$priming2 <- seurat$priming
seurat$priming2[which(seurat$numclust == "ifn")] <- "primed" 

seuratOrdered$priming2 <- seurat$priming
seuratOrdered$priming2[which(seuratOrdered$numclust == "ifn")] <- "primed" 

Idents(seuratOrdered) <- "priming2"
Idents(seurat) <- "priming"
VlnPlot(seurat,features = selectedTF,pt.size = 0.1)

Idents(seurat) <- "priming"

FindMarkers(seurat,features = c("Tet2","Dnmt3a","Sp1","Sirt1","Rb1"),ident.1 = "non primed",logfc.threshold = 0,min.pct = 0)

seuratNp <- subset(seurat,idents = "primed")
Idents(seuratNp) <- "AGE"
FindConservedMarkers(seuratNp,features = c("Tet2","Dnmt3a","Sp1","Sirt1","Rb1"),grouping.var = "platform", ident.1 = "Old",logfc.threshold = 0,min.pct = 0)
Idents(seurat) <- "AGE"

FindConservedMarkers(seurat,features = c("Tet2","Dnmt3a","Sp1","Sirt1","Rb1"),grouping.var = "platform", ident.1 = "Old",logfc.threshold = 0,min.pct = 0)

```

## View selected TF in violins
```{r, fig.height=14,fig.width=15}
DefaultAssay(seuratOrdered) <- "RNA"
selectedTF <- c("Sirt1","Pten","Tgfb1","Tgfb2","Tgfb3")
VlnPlot(seuratOrdered,features = selectedTF,pt.size = 0.1,split.by = "AGE")
```



```{r ,fig.height = 12}
Idents(seuratOrdered) <- "numclust"
DefaultAssay(seuratOrdered) <- "RNA"
selectedTF <- c("Gata2","Zfpm1","Ikzf1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Ets1","Sp1")
selectedTF <- c("Egr1","Bmi1","Dnmt3a","Tet2","Epor","Txnip","Smad2","Ezh1","E2f4")
selectedTF <- c("Ring1","Pcgf1")
selectedTF <- c("Ezh2","Suz12","Eed","Ring1","Pcgf1","Cbx7","Dnmt3a")
selectedTF <- c("Ebf1","Tet3","Uhrf1","Uhrf2","Cxxc4","Sirt1")

selectedTF <- c("Gata2","Zfpm1","Ikzf1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Ets1","Sp1")

selectedTF <- c("Ptger4","Ptk2","Myc","Dnmt3a","Sirt2","Sirt3","Uhrf2","Sp1","Uhrf1")

VlnPlot(seuratOrdered,features = selectedTF,pt.size = 0.1,split.by = "AGE")
VlnPlot(seuratOrdered,features = selectedTF,pt.size = 0.1)

```


```{r}
Idents(seurat) <- "numclust"
npMarkers <- FindAllMarkers(seurat,logfc.threshold = 0,min.pct = 0)

seuratNP <- subset(x = seurat, idents = 'tgf')
Idents(seuratNP) <- "AGE"
npAging <- FindConservedMarkers(seuratNP,logfc.threshold = 0,min.pct = 0,grouping.var = "platform",ident.1 = "Old")
remove(seuratNP)

importantMarkers <- c("Cdkn1a","Tet2","Dnmt3a","Junb","Sp1")

importantMarkers %in% rownames(tgfAging)

DimPlot(seurat,reduction = "umap",label = T)
```



```{r fig.height=14,fig.width=30}
DefaultAssay(seuratOrdered) <- "AUCellRNA"
selectedTF <- c("Gata2","Zfpm1","Ikzf1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Gfi1b","Egr1","Junb","Zbtb16","Mycn")
VlnPlot(seuratOrdered,features = paste0(c(selectedTF),"(+)"),pt.size = 0,ncol = 3)
VlnPlot(seuratOrdered,features = paste0(c(selectedTF),"(-)"),split.by = "sampleName",pt.size = 0,ncol =3)

```
## Load regulons targets

```{r}
regulons <- RJSONIO::fromJSON("../output/ScenicRNA/cis_target_maskDropouts/regulons.json")

regulons <- regulons[which(endsWith(names(regulons),"(+)"))]

# Interaction table of positive regulons and their target genes
regulonsTable<- matrix(ncol = 2)

for (i in names(regulons)) {
  add <- cbind(rep(i,length(regulons[[i]])),regulons[[i]])
  regulonsTable<- rbind(regulonsTable,add)
}
regulonsTable<- regulonsTable[-1,]

colnames(regulonsTable) <- c("regulon","gene")
regulonsTablePos <- as.data.frame(regulonsTable)


# keep only the name of the tf for the regulons

regulonsTablePos$regulon <- str_split_fixed(regulonsTablePos$regulon,"\\(",n=2)[,1]
```


```{r}

regulons <- RJSONIO::fromJSON("../output/ScenicRNA/cis_target_maskDropouts//regulons.json")

regulons <- regulons[which(endsWith(names(regulons),"(-)"))]
# Interaction table of negative regulons and their target genes
regulonsTable<- matrix(ncol = 2)

for (i in names(regulons)) {
  add <- cbind(rep(i,length(regulons[[i]])),regulons[[i]])
  regulonsTable<- rbind(regulonsTable,add)
}
regulonsTable<- regulonsTable[-1,]

colnames(regulonsTable) <- c("regulon","gene")
regulonsTableNeg <- as.data.frame(regulonsTable)


# keep only the name of the tf for the regulons

regulonsTableNeg$regulon <- str_split_fixed(regulonsTableNeg$regulon,"\\(",n=2)[,1]
```

```{r fig.height=7.5,fig.width=7}

regulonsTableNeg$mor <- "-"
regulonsTablePos$mor <- "+"

regulonsTable <- rbind(regulonsTableNeg,regulonsTablePos)

selectedGenes <- c("Gata2","Zfpm1","Ikzf1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Myc","Egr1","Junb")

CDK46CycD <- c("Cdk4","Cdk6","Ccnd1","Ccnd2","Ccnd3")

RegulonCDK46CycD <- regulonsTable[which(regulonsTable$regulon %in% selectedGenes & regulonsTable$gene %in% CDK46CycD),c("regulon","gene","mor")]

RegulonCDK46CycD$gene <- "CDK46CycD"

CIPKIP <- c("Cdkn1b","Cdkn1a","Cdkn1c")

RegulonCIPKIP <- regulonsTable[which(regulonsTable$regulon %in% selectedGenes & regulonsTable$gene %in% CIPKIP),c("regulon","gene","mor")]

RegulonCIPKIP$gene <- "CIPKIP"


INK4 <-c("Cdkn2a","Cdkn2b","Cdkn2c","Cdkn2d")

RegulonINK4 <- regulonsTable[which(regulonsTable$regulon %in% selectedGenes & regulonsTable$gene %in% INK4),c("regulon","gene","mor")]

#RegulonINK4$gene <- "INK4"

scenicNet <- regulonsTable[which(regulonsTable$regulon %in% selectedGenes & regulonsTable$gene %in% selectedGenes),c("regulon","gene","mor")]

 #scenicNet[which(duplicated(scenicNet[,c(1,2)],fromLast=FALSE)|duplicated(scenicNet[,c(1,2)],fromLast=TRUE)),]

scenicNet <- rbind(scenicNet,RegulonCDK46CycD,RegulonCIPKIP,RegulonINK4)


scenicGraph<- graph_from_data_frame(scenicNet,directed = TRUE, vertices = NULL)

edges.rnaMaskDrop <- scenicNet[,"mor"]
edges.color.rnaMaskDrop <- rep("red",length(edges.rnaMaskDrop))
edges.color.rnaMaskDrop[which(edges.rnaMaskDrop == "+")] <- "blue"

plot(scenicGraph, 
     vertex.size =30,
     vertex.shape = "rectangle",
     edge.color = edges.color.rnaMaskDrop,
vertex.label.cex = 1.5,layout=layout.circle)


handmadeNet <- read.table("../publicData/smallNet.reggraph",sep = " ",stringsAsFactors  = F)
colnames(handmadeNet) <- c("regulon","mor","gene")
handmadeNet$mor[which(handmadeNet$mor == "-|")] <- "-"
handmadeNet$mor[which(handmadeNet$mor == "->")] <- "+"

for (r in c(1:dim(handmadeNet)[1])) {
  print(handmadeNet[,])
}

influenceGraph <- rbind(scenicNet,handmadeNet,stringsAsFactors  = F)
influenceGraph$mor[which(influenceGraph$mor == "-")] <- "-1"
influenceGraph$mor[which(influenceGraph$mor == "+")] <- "1"


#newTFSelection <- c("Gata2","Zfpm1","Ikzf1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Dnmt3a","Tet2","Egr1","Junb")
newTFSelection <- c("Gata2","Zfpm1","Ikzf1","Klf1","Cebpa","Gata1","Fli1","Tal1","Spi1","Egr1","Junb")
influenceGraph <- influenceGraph[which(influenceGraph$gene %in% newTFSelection & influenceGraph$regulon %in% newTFSelection),]
#   
# influenceGraph$regulon[which(influenceGraph$regulon %in% c("Dnmt3a","Tet2"))] <- "Dnmt3a_Tet2"
# 
# influenceGraph$gene[which(influenceGraph$gene %in% c("Dnmt3a","Tet2"))] <- "Dnmt3a_Tet2"

write.table(influenceGraph,file = "influenceGraphForBonesis.tsv",quote = F,sep = "\t",row.names = F)
write.table(handmadeNet,file = "influenceGraph0ForBonesis.tsv",quote = F,sep = "\t",row.names = F)


```


```{r, fig.heigth = 40,fig.width=20}
allGenes <- unique(c(influenceGraph$regulon,influenceGraph$gene))

VlnPlot(seurat,features = allGenes)

```


```{r}
 VlnPlot(seurat,features = "Hdac2",split.by = "AGE")
```

## Test Saran code to write ASP graph here

```{r}
maxClause <- 3
network <- influenceGraphTableMin
colnames(network) <- c("TF","target","interaction")

asp <- data.frame()
nb <- union(network$TF,network$target)
asp <- paste('nbnode(',length(union(network$TF,network$target)),').', sep = '')
for(i in 1:length(nb)){
  asp <- rbind(asp,
  	paste('node("',nb[i],'").', 
  	sep = ''))
}
for(i in 1:dim(network)[1]){
  asp <- rbind(asp,
  	paste('in("',network$TF[i],'","',network$target[i],'",',network$interaction[i],").", 
  	sep = ''))
}

n <- dim(network[network$target==nb[i],])[1]
k <- min(dim(combn(n,floor(n/2)))[2],maxClause)

for(i in 1:length(nb)){
  asp <- rbind(asp,
  	paste('maxC("',nb[i],'",',k,').', 
  	sep = ''))
}

# be careful if launched several time it will append rows to existing file
write.table(asp, file = "../output/ASP/inlfuenceGraphMin.asp", 
	quote = FALSE, 
	row.names = FALSE, 
	col.names = FALSE,
	append = F)

```

## Write influence graph with Bonzanni interaction

```{r}
network <- influenceGraphTable
colnames(network) <- c("TF","target","interaction")

asp <- data.frame()
nb <- union(network$TF,network$target)
asp <- paste('nbnode(',length(union(network$TF,network$target)),').', sep = '')
for(i in 1:length(nb)){
  asp <- rbind(asp,
  	paste('node("',nb[i],'").', 
  	sep = ''))
}

n <- dim(network[network$target==nb[i],])[1]
k <- max(dim(combn(n,floor(n/2)))[2],maxClause)

for(i in 1:length(nb)){
  asp <- rbind(asp,
  	paste('maxC("',nb[i],'",',k,').', 
  	sep = ''))
}
for(i in 1:length(nb)){
  asp <- rbind(asp,
  	paste('maxC("',nb[i],'",',dim(network[network$target==nb[i],])[1],').', 
  	sep = ''))
}

# be careful if launched several time it will append rows to existing file
write.table(asp, file = "../output/ASP/inlfuenceGraphMin.asp", 
	quote = FALSE, 
	row.names = FALSE, 
	col.names = FALSE,
	append = F)
```

```{r}

selectedGenes <- c("Ccnd1","Ccnd2","Cdk4","Cdk6")
ptBranchingM <- max(pData(monocle)[which(pData(monocle)$State ==3),"Pseudotime"])

genePseudotime <- function(gene, monocle1,monocle2) {
  
  p1 <- plot_genes_in_pseudotime(monocle1[gene],vertical_jitter = 0.01) +
    scale_color_manual(values = colorTrajStateFinal)  +
    theme(legend.position = "right",
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) + 
    NoLegend()+
    geom_vline(xintercept = ptBranchingM,color = "red",linetype = "dashed",size =1) +
    theme(strip.text = element_text(face = "italic")) 
  
  p2 <- plot_genes_in_pseudotime(monocle2[gene],vertical_jitter = 0.01) +
    scale_color_manual(values = colorTrajStateFinal) + 
    theme(legend.position = "right",
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) + 
    NoLegend()+
    geom_vline(xintercept = ptBranchingM,color = "red",linetype = "dashed",size = 1) 
  #+
  #  facet_wrap(~feature_label,labeller=labeller,nrow = 1, 
  #             ncol = 6, scales = "free_y") 
  
  p1$labels$x <- "Pseudotime"
  p2$labels$x <- "Pseudotime"
  
  youngLim <- exp(ggplot_build(p1)$layout$panel_params[[1]]$y.range*log(10)) 
  
  oldLim <- exp(ggplot_build(p2)$layout$panel_params[[1]]$y.range*log(10)) 
  
  
  if(which.max(c(youngLim[2],oldLim[2]))==1) {
    p2 <- p2 + scale_y_log10(limits = youngLim)
    p1 <- p1 + scale_y_log10(limits = youngLim)
  } else{
    p2 <- p2 + scale_y_log10(limits = oldLim)
    p1 <- p1 + scale_y_log10(limits = oldLim)
  }
  
  p2 <- p2 +  theme(strip.text = element_text(face = "italic"))
  p <-  arrangeGrob(p1+NoLegend(),blank,p2+NoLegend(),blank,heights = c(2,0.2,2,0.2))
  #p <-  arrangeGrob(p1,p2)
  return(p)
}
colorTrajStateFinal <- c("#999999", "#E69F00", "#56B4E9", "#009E73","#F0E442")

blank <- grid.rect(gp=gpar(col="white"),draw = F)

fig6G_plots <- lapply(selectedGenes,genePseudotime,monocle1 = monocle[,which(pData(monocle)$AGE == "Young")],monocle2 = monocle[,which(pData(monocle)$AGE == "Old")])



source("../../herault_et_al/scHSC_herault/R_src/funForPlot.R")

legendPt <- g_legend(plot_genes_in_pseudotime(monocle["Ccnb1"]) + scale_color_manual(values = colorTrajStateFinal)  + guides(colour = guide_legend(override.aes = list(size=5))) +
                       theme(legend.text = element_text(size = 14))+theme(legend.position = "bottom"),"horizontal")

grid6G <- grid.arrange(arrangeGrob(fig6G_plots[[1]],
                                   fig6G_plots[[2]],
                                   fig6G_plots[[3]],
                                   fig6G_plots[[4]],
                                   ncol = 4),legendPt,ncol = 1 , heights = c(20,1))

```

```{r}
plot(genePseudotime(gene = "Junb",monocle1,monocle2))
grid.arrange(plot_genes_in_pseudotime(monocle1[selectedGenes],vertical_jitter = 0.01,ncol = 4),
plot_genes_in_pseudotime(monocle2[selectedGenes],vertical_jitter = 0.01,ncol = 4))
```

